---
title: "CleanInsectData"
output: html_document
date: "2024-01-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Goals
- Import annotations, drop list and metadata 
- Use droplist to remove 512 images from 2021 at Site FF06-2022 (SD card was not formatted when it was placed in the camera)
- Combine with metadata using FileName 
- Filter to only include Nocturnal images 


### Setting up work space 
```{r}
library(data.table)
library(tidyverse)
library(beepr)
library(lubridate)
library(purrr)
library(janitor)
#renv::install("rstudio/renv")
library(renv)
library(stringr)
library(kableExtra)
library(papeR)
library(skimr)
library(vtable)
library(ggdark)
library(beepr)
library(readr)

## Setup output directory 
output <- "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/ForDryad/1.DataCleaning/InsectData/Outputs"

file.name <- "CleanInsectData"

todays_date <- Sys.Date()
 
dir.name <- str_c(output,"/", file.name, "_", todays_date)
dir.name
 
output_today <- dir.name
output_today

dir.create(output_today)
output_today
# "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/ForDryad/1.DataCleaning/InsectData/Outputs/CleanInsectData_2024-02-01"

```

## Import data - remove the droplist images - match (relevant) metadata to annotatoins
```{r}

# Annotations for all sites combined
annot <- read_delim("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/ForDryad/1.DataCleaning/InsectData/Inputs/fullannotations_metadata_combined_OCT_FF22.csv", 
     delim = ",", escape_double = FALSE, col_types = cols(...1 = col_skip()),
     trim_ws = TRUE)
dim(annot)
# 5474    136

## Select most relevant columns 
annot1 <- annot %>% select(c(FileName, file_size, file_attributes, 
                             region_count, region_id,  
                             region_shape_attributes, region_attributes, 
                             SourceFile, datetime))

dim(annot1)
# 5474    9
# This is much more manageable

```



## Explore and clean the new combined annotations/metafile
```{r}
## Create site and date columns 
annot3 <- annot1 %>% 
  dplyr::mutate(Site = case_when(
  str_detect(FileName, "FF01") ~ "FF01",
  str_detect(FileName, "FF02") ~ "FF02", 
  str_detect(FileName, "FF03") ~ "FF03",
  str_detect(FileName, "FF04") ~ "FF04",
  str_detect(FileName, "FF05") ~ "FF05",
  str_detect(FileName, "FF06") ~ "FF06",
  str_detect(FileName, "FF07") ~ "FF07",
  str_detect(FileName, "FF08") ~ "FF08",
  str_detect(FileName, "FF09") ~ "FF09",
  str_detect(FileName, "FF10") ~ "FF10",
  str_detect(FileName, "FF11") ~ "FF11")) %>% 
  dplyr::mutate(Site = factor(Site)) %>% 
  dplyr::mutate(date = as.Date(datetime))
summary(annot3)
summary(annot3$Site)
#FF01 FF02 FF03 FF04 FF05 FF06 FF07 FF08 FF09 FF10 FF11 
# 713  478   48  729  434  277  526  193  676  903  497 


## Quality control check 
# ggplot(annot3) + geom_bar(aes(x = Site, fill = Site), stat = "count")
# 
# ggplot(annot3) + geom_point(aes(x = date , color = Site), size = 3, stat = "count") + facet_wrap(~Site) + theme()
```


## Clean the annotatoin columns so that these can be combined with the 2021 dataset 
```{r}
head(annot3$file_attributes)

annot4 <- annot3 %>% 
  dplyr::select(-c(file_size, region_shape_attributes)) %>% 
  dplyr::mutate(ImageQuality = factor(case_when(
                  str_detect(file_attributes, "Good") ~ "Good",
                  str_detect(file_attributes, "Poor") ~ "Poor",
                  str_detect(file_attributes, "Bad") ~ "Bad"))) %>% 
  dplyr::select(-file_attributes) %>% 
  dplyr::mutate(Certain = factor(case_when(
    str_detect(region_attributes, "Yes") ~ "Yes", 
    str_detect(region_attributes, "No") ~ "No",
    TRUE ~ "NoInsects"))) %>% 
  dplyr::select(-region_attributes) %>% 
  rename(Region_count = region_count) %>% 
  mutate(date = as.Date(datetime), 
         nighttime = datetime - 12*60*60,
         night = as.Date(nighttime)) 

summary(annot4$ImageQuality) # Nice 
 # Bad Good Poor 
 # 522 4526  426 

summary(annot4$Certain) 
      #  No NoInsects       Yes 
      # 689      3551      1234 

##  Calculate for each image: 
# "nInsects" = number of certain = yes 
# "nUncertain"  = number of certain = no 

annot5 <- annot4 %>% 
  dplyr::group_by(FileName) %>% 
  dplyr::summarize(nInsects = sum(Certain == "Yes"),
                   nUncertain = sum(Certain == "No")) 

annot4.5 <- annot4 %>% 
  dplyr::select(-c(region_id, Certain)) %>% distinct() 
# removes rows of duplicate images 

annot6 <- left_join(annot5, annot4.5)
annot6$SiteYear <- factor(paste0(annot6$Site, "-2022")) 

bugs22 <- annot6 %>% select(-Site)

effort22 <- bugs22 %>% 
  group_by(SiteYear, night) %>% 
  dplyr::summarize(nPhotos = sum(n())) 

bugeffort <- left_join(bugs22, effort22)

bugs2022 <- bugeffort %>% select(-c(SourceFile) ) 

summary(bugs2022)
```



## Combine with 2021 data 
```{r}
bugs21 <- read_csv("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/ForDryad/1.DataCleaning/InsectData/Inputs/combinedannotationsFF21w_locations_wmetadata.csv")
dim(bugs21)
# 17046    17

bugs21 <- bugs21 %>% dplyr::select(-c(...1, ...2, Site.y, Latitude, Longitude, Type, SiteType, Date, Time)) %>% rename(Site = Site.x, FileName = Filename) %>% mutate(Site = factor(Site)) 

bugs21$datetime <- as.POSIXct(bugs21$DateTimeOriginal, 
                                    format = "%Y:%m:%d %H:%M:%OS", 
                              tz = "Europe/Berlin")
bugs21$date <- as.Date(bugs21$datetime)

names(bugs21)
head(bugs21)

summary(bugs21$Site)
#  FF1 FF10 FF11 FF12  FF2  FF3  FF4  FF5  FF6  FF7  FF8  FF9 
# 1750 1476  999 1542 1620 1018 1964  957  972 1760 1331 1657

bugs21$ImageQuality <- factor(bugs21$ImageQuality)

names(bugs21)
#  [1] "FileName"         "nInsects"         "nUncertain"      
#  [4] "Site"             "Region_count"     "ImageQuality"    
#  [7] "Annotator"        "DateTimeOriginal" "datetime"        
# [10] "date"

bugs21$SiteYear <- factor(paste0(bugs21$Site, "-2021")) 

bugs21.1<- bugs21 %>% 
  select(-c(Site, Annotator, DateTimeOriginal)) %>% 
  mutate( nighttime = datetime - 12*60*60,
         night = as.Date(nighttime)) 

effort21 <- bugs21.1 %>% 
  group_by(SiteYear, night) %>% 
  dplyr::summarize(nPhotos = sum(n())) 

bugs2021 <- left_join(bugs21.1, effort21)



names(bugs2021)
dim(bugs2021)
# 17046
names(bugs2022)
dim(bugs2022)
# 4755

bugs <- full_join(bugs2022, bugs2021)
dim(bugs)
# 21801    11
# 4755 + 17046 = 21801, good!


#write.csv(bugs, file = file.path(output_today, "OCT_imageannotations_withmeta_combined.csv"))

`````````
