---
title: "HemispherePhotoAnalysis"
output: html_document
date: "2024-01-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
##########          Hemiphot.R         ##########
# This script is intended to calculate light indices and more from hemispherical images
# read the manual and helpfile to use this script.
# HemiphotTest.R provides examples of all single calculations
# HemiphotBatch.R provides examples of batch calculations for a 
# number of images in one directory
#
# to be able to use Hemophot.R yo will need to install the functions
# with the command >source("Hemiphot.R")
# provided the script is foudn in our working directory
#######END          Hemiphot.R         ##########





##########          How to cite the use of Hemiphot         ##########
#If you use Hemiphot.R for your research or work please cite as:
#Hans ter Steege (2018) Hemiphot.R: Free R scripts to analyse hemispherical 
#photographs for canopy openness, leaf area index and photosynthetic 
#active radiation under forest canopies.  
#Unpublished report. Naturalis Biodiversity Center, Leiden, The Netherlands
#https://github.com/Hans-ter-Steege/Hemiphot
#######END          How to cite the use of Hemiphot         ##########





### This is the batch script for Hemiphot.R
### Here you can run all functions and store 
### all data by file


###### NOTES ########

# This script is modified to suit data collected for the Follo Forest Project from the summer of 2021 and 2022 to calculate Canopy Openness (CO) and Leaf Area Index (LAI). Simple visualizations and preliminary analyses comparing these values across sites are included here as well. 

###############################################

##########          load libraries and source files          ##########
library(tidyverse)
library(cowplot)
library(scales)
library(dplyr)
library(jpeg) 
library(lme4)
library(ggpmisc)
source("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/Hemisphere Photos/Hemiphot.R")        # functions to calculate all results

#remotes::install_github("coolbutuseless/ggpattern")
library(ggpattern)

## Setup output directory 
output <- "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/ForDryad/1.DataCleaning/HemispherePhotos"

file.name <- "HemispherePhotoAnalysis"

todays_date <- Sys.Date()
 
dir.name <- str_c(output,"/", file.name, "_", todays_date)
dir.name
 
output_today <- dir.name
output_today

dir.create(output_today)
output_today
# "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/ForDryad/1.DataCleaning/HemispherePhotos/HemispherePhotoAnalysis_2024-01-31"


```


## 2021 data 
```{r}
##########          initialize site and image data          ##########

# These paramenters are not relevant to calculating Canopy Openness or Leaf Area Index. Default / example paraemters kept here for future reference. 

### Location parameters

#days = seq(15,360,30)   # roughly each mid of the 12 months

#location.latitude   = 1.487
#location.altitude   = 0
#location.day        = 150
#location.days       = seq(15,360,30)   # roughly each mid of the 12 months

### Image parameters
## determine in Hemiphot.R and fill in here for batch processing
location.cx         = 1504             # x coordinate of center
location.cy         =  975             # y coordinate of center
location.cr         =  900             # radius of circle
location.threshold  = 0.65

### atmospheric parameters
# location.tau = 0.6 
# Between 0.1 and 1.0, default 0.6. The transmission of 1 optical
# airmass (use 1.0 if you want to know the amount of light on top of
# the atmosphere). Input as decimal.
# location.uoc = 0.15
# Uniform Overcast Sky

#######END          initialize site and image data          ##########






##########          load image namess          ##########

### We assume colour images
### in a subdirectory images
### load all JPG file names in a list

all.images = list.files(path="C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/Hemisphere Photos/HemispherePhotosEdited2021", pattern = ".jpg")

nr.images = length(all.images); nr.images

## Create data frame to hold all results 

### ** Modified to only include CanOpen and LAI ** 

all.data = data.frame(matrix(0, nr.images, 3))
names(all.data) = c("File", "CanOpen", "LAI")
all.data[,1] = all.images

## now the batch can start
#t1 = Sys.time()
for(i in 1:nr.images){    
  ## read file
  image = readJPEG(paste("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/Hemisphere Photos/HemispherePhotosEdited2021/", all.images[i],sep = ""), native = F)     
  ## if native = T creates a raster, else an array
  
  ## conver to Hemi image
  image = Image2Hemiphot(image)
  
  ## select blue channel
  image = SelectRGB(image, "B")
  
  #threshold
  image = ThresholdImage(im = image, th = location.threshold, draw.image = F)
  
  # canopy openness
  gap.fractions = CalcGapFractions(image)
  all.data[i,2] = CalcOpenness(fractions = gap.fractions)
  
  ## calculate LAI according to Licor's LAI Analyzer 
  all.data[i,3] = CalcLAI(fractions = gap.fractions)
}

#t2 = Sys.time()


##time per image
#(t2 - t1)/nr.images
#Time difference of 0.XXXX secs

head(all.data)

## save data
#write.csv(all.data, file = file.path(output_today, "HemiphotOutput.65_final2021.csv"))


####################################################

# Create a new column to distinguish between site types 

######################  H65  ########################

H65 <- all.data
H65 <- as_tibble(H65)

# Create a new column to distinguish between site types 

H65 %>%  
  mutate(Type = case_when(
    endsWith(File, "_IB.jpg") ~ "Interior Forest",
    endsWith(File, "_OB.jpg") ~ "Open Forest",
    endsWith(File, "_CB.jpg") ~ "Canopy Forest"
  )) -> H65
H65$Type <- as.factor(H65$Type)
head(H65)

# Create a new column to distinguish between site names 

H65$Site <- sub("_IB.jpg", "", H65$File)
H65$Site <- sub("_OB.jpg", "", H65$Site)
H65$Site <- sub("_CB.jpg", "", H65$Site)
H65$Site <- as.factor(H65$Site)

head(H65)
 
#Subset data based on site type 

H65 %>% filter(Type == "Interior Forest") -> H65_IB
summary(H65_IB$CanOpen)
 #   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 # 0.0940  0.2015  0.2409  0.2343  0.2570  0.3759 


print(var(H65_IB$CanOpen))
# 0.004751281
print(sd(H65_IB$CanOpen))
# 0.06892954

H65 %>% filter(Type == "Open Forest") -> H65_OB
summary(H65_OB$CanOpen)
 #   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 # 0.1601  0.2526  0.2896  0.3074  0.3654  0.4498 

print(var(H65_OB$CanOpen))
# 0.008162474
print(sd(H65_OB$CanOpen))
# 0.09034641


######################################################


########### Visualizing Canopy Openness #############
head(H65)
dev.off()
M65 <- H65 %>% ggplot() + geom_density(aes(x = CanOpen, fill = Type), alpha = 0.2) + ggtitle("Theshold = 0.65") 


M65

######################################################

g65 <- 
  ggplot(H65, aes(x=File, y=CanOpen, fill=Site, pattern=Type)) +
  geom_bar_pattern(stat="identity", position=position_dodge(preserve = "single"),
                   color = "black", 
                   pattern_fill = "black",
                   pattern_angle = 45,
                   pattern_density = 0.1,
                   pattern_spacing = 0.025,
                   pattern_key_scale_factor = 0.6) + 
  scale_pattern_manual(values = c("Interior Forest" = "stripe", "Open Forest" = "none"))+
  scale_fill_brewer(palette="Paired")+
  theme_minimal() + 
  ggtitle("Theshold = 0.65") + 
  scale_x_discrete(name = "Sites", 
  labels = c("FF1", " " , "FF2", " ", "FF3", " ", "FF4", " ", "FF5", " ", "FF6", " ", "FF7", " ", "FF8", " ", "FF9", " ", "FF10", " ", "FF11", " ", "FF12", " ")) +
  guides(pattern = guide_legend(override.aes = list(fill = "white")),
         fill = guide_legend(override.aes = list(pattern = "none")))

g65

####################################################################


################# Visualizing Leaf Area Index ######################

l65 <- ggplot(H65, aes(LAI, fill = Type))

L65 <- l65 + geom_density(alpha=0.2) + ggtitle("Theshold = 0.65") + theme(legend.position = "none")


L65



p65 <- 
  ggplot(H65, aes(x=File, y=LAI, fill=Type)) +
  geom_bar(stat="identity", position=position_dodge())+
  scale_fill_brewer(palette="Paired")+
  theme_minimal() + 
  ggtitle("Theshold = 0.65") + 
  scale_x_discrete(name = "Sites", 
                   breaks = c("FF1-IB.JPG", "FF1-OB.JPG",  "FF10-IB.JPG", "FF10-OB.JPG", "FF11-IB.JPG", "FF11-OB.JPG", "FF12-IB.JPG", "FF12-OB.JPG",  "FF2-IB.JPG", "FF2-OB.JPG",  "FF3-IB.JPG", "FF3-OB.JPG", "FF4-IB.JPG", "FF4-OB.JPG", "FF5-IB.JPG", "FF5-OB.JPG",  "FF6-IB.JPG", "FF6-OB.JPG", "FF7-IB.JPG", "FF7-OB.JPG", "FF8-IB.JPG",  "FF8-OB.JPG",  "FF9-IB.JPG",  "FF9-OB.JPG"), 
                   labels = c("FF1", " " , "FF2", " ", "FF3", " ", "FF4", " ", "FF5", " ", "FF6", " ", "FF7", " ", "FF8", " ", "FF9", " ", "FF10", " ", "FF11", " ", "FF12", " ")) +
  theme(legend.position = "none") 

p65



P65 <- 
  ggplot(H65, aes(x=File, y=LAI, fill=Site, pattern=Type)) +
  geom_bar_pattern(stat="identity", position=position_dodge(preserve = "single"),
                   color = "black", 
                   pattern_fill = "black",
                   pattern_angle = 45,
                   pattern_density = 0.1,
                   pattern_spacing = 0.025,
                   pattern_key_scale_factor = 0.6) + 
  scale_pattern_manual(values = c(
    "Interior Forest" = "stripe", "Open Forest" = "none"))+
  scale_fill_brewer(palette="Paired")+
  theme_minimal() + 
  ggtitle("Theshold = 0.65") + 
  scale_x_discrete(name = "Sites", 
                   labels = c("FF1", " " , "FF2", " ", "FF3", " ", "FF4", " ", "FF5", " ", "FF6", " ", "FF7", " ", "FF8", " ", "FF9", " ", "FF10", " ", "FF11", " ", "FF12", " ")) +
  guides(pattern = guide_legend(override.aes = list(fill = "white")),
         fill = guide_legend(override.aes = list(pattern = "none")))

P65

H65.21 <- H65

```



## 2022 data 
```{r}

all.images = list.files(path="C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/Hemisphere Photos/HemispherePhotosEdited2022/", pattern = ".jpg")

nr.images = length(all.images); nr.images

## Create data frame to hold all results 

### ** Modified to only include CanOpen and LAI ** 

all.data = data.frame(matrix(0, nr.images, 3))
names(all.data) = c("File", "CanOpen", "LAI")
all.data[,1] = all.images

## now the batch can start
#t1 = Sys.time()
for(i in 1:nr.images){    
  ## read file
  image = readJPEG(paste("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/Hemisphere Photos/HemispherePhotosEdited2022/", all.images[i],sep = ""), native = F)     
  ## if native = T creates a raster, else an array
  
  ## conver to Hemi image
  image = Image2Hemiphot(image)
  
  ## select blue channel
  image = SelectRGB(image, "B")
  
  #threshold
  image = ThresholdImage(im = image, th = location.threshold, draw.image = F)
  
  # canopy openness
  gap.fractions = CalcGapFractions(image)
  all.data[i,2] = CalcOpenness(fractions = gap.fractions)
  
  ## calculate LAI according to Licor's LAI Analyzer 
  all.data[i,3] = CalcLAI(fractions = gap.fractions)
}

#t2 = Sys.time()


##time per image
#(t2 - t1)/nr.images
#Time difference of 0.XXXX secs

head(all.data)

## save data
#write.csv(all.data, file = file.path(output_today, "HemiphotOutput.65_final2022.csv")) 

############ Compare different thresholds ############

# Create a new column to distinguish between site types 

######################  H65  ########################

H65 <- all.data
H65 <- as_tibble(H65)

# Create a new column to distinguish between site types 

H65 %>%  
  mutate(Type = case_when(
    endsWith(File, "_IB.jpg") ~ "Interior Forest",
    endsWith(File, "_OB.jpg") ~ "Open Forest",
    endsWith(File, "_CB.jpg") ~ "Canopy Forest"
  )) -> H65
H65$Type <- as.factor(H65$Type)
head(H65)

# Create a new column to distinguish between site names 

H65$Site <- sub("_IB.jpg", "", H65$File)
H65$Site <- sub("_OB.jpg", "", H65$Site)
H65$Site <- sub("_CB.jpg", "", H65$Site)
H65$Site <- as.factor(H65$Site)

head(H65)
 
#Subset data based on site type 

H65 %>% filter(Type == "Interior Forest") -> H65_IB
summary(H65_IB$CanOpen)
#    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
# 0.09473 0.12834 0.17544 0.17768 0.22686 0.25349 


print(var(H65_IB$CanOpen))
# 0.0034318
print(sd(H65_IB$CanOpen))
# 0.05858157

H65 %>% filter(Type == "Open Forest") -> H65_OB
summary(H65_OB$CanOpen)
#    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#  0.1709  0.2863  0.3582  0.3577  0.4152  0.5349 
print(var(H65_OB$CanOpen))
# 0.01186248
print(sd(H65_OB$CanOpen))
# 0.108915

H65 %>% filter(Type == "Canopy Forest") -> H65_OB
summary(H65_OB$CanOpen)
 # 0.1024  0.1807  0.2251  0.2329  0.2778  0.4345

######################################################


########### Visualizing Canopy Openness #############
head(H65)
#dev.off()
M65 <- H65 %>% ggplot() + geom_density(aes(x = CanOpen, fill = Type), alpha = 0.2) + ggtitle("Theshold = 0.65") 


M65

######################################################

g65 <- 
  ggplot(H65, aes(x=File, y=CanOpen, fill=Site, pattern=Type)) +
  geom_bar_pattern(stat="identity", position=position_dodge(preserve = "single"),
                   color = "black", 
                   pattern_fill = "black",
                   pattern_angle = 45,
                   pattern_density = 0.1,
                   pattern_spacing = 0.025,
                   pattern_key_scale_factor = 0.6) + 
  scale_fill_brewer(palette="Paired")+
  theme_minimal() + 
  ggtitle("Theshold = 0.65") + 
  scale_x_discrete(name = "Sites", 
  labels = c("FF1", " " , " " ,"FF2", " ", " " , 
             "FF3", " ", " " , "FF4", " " , " ", 
             "FF5", " " , " ", "FF6", " " , " ", 
             "FF7"," " , " ", "FF8", " " , " ", 
             "FF9"," " , " ", "FF10", " " ," ", 
             "FF11", " "," " )) +
  guides(pattern = guide_legend(override.aes = list(fill = "white")),
         fill = guide_legend(override.aes = list(pattern = "none")))

g65

####################################################################


################# Visualizing Leaf Area Index ######################

l65 <- ggplot(H65, aes(LAI, fill = Type))

L65 <- l65 + geom_density(alpha=0.2) + ggtitle("Theshold = 0.65") + theme(legend.position = "none")


L65



p65 <- 
  ggplot(H65, aes(x=File, y=LAI, fill=Type)) +
  geom_bar(stat="identity", position=position_dodge())+
  scale_fill_brewer(palette="Paired")+
  theme_minimal() + 
  ggtitle("Theshold = 0.65")  +
  theme(legend.position = "none") 

p65



P65 <- 
  ggplot(H65, aes(x=File, y=LAI, fill=Site, pattern=Type)) +
  geom_bar_pattern(stat="identity", position=position_dodge(preserve = "single"),
                   color = "black", 
                   pattern_fill = "black",
                   pattern_angle = 45,
                   pattern_density = 0.1,
                   pattern_spacing = 0.025,
                   pattern_key_scale_factor = 0.6) + 
  scale_fill_brewer(palette="Paired")+
  theme_minimal() + 
  ggtitle("Theshold = 0.65") + 
  guides(pattern = guide_legend(override.aes = list(fill = "white")),
         fill = guide_legend(override.aes = list(pattern = "none")))

P65

H65.22 <- H65

```


## Combine the two years 
```{r}

H65.21 <- read_csv("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/ForDryad/1.DataCleaning/HemispherePhotos/HemispherePhotoAnalysis_2024-01-31/HemiphotOutput.65_final2021.csv", 
     col_types = cols(...1 = col_skip()))
head(H65.21)
#   File        CanOpen   LAI
#   <chr>         <dbl> <dbl>
# 1 FF01_IB.jpg  0.243   2.34
# 2 FF01_OB.jpg  0.160   4.24
# 3 FF02_IB.jpg  0.236   2.76
# 4 FF02_OB.jpg  0.307   2.52
# 5 FF03_IB.jpg  0.0940  4.45
# 6 FF03_OB.jpg  0.253   2.88

H65.22 <- read_csv("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/ForDryad/1.DataCleaning/HemispherePhotos/HemispherePhotoAnalysis_2024-01-31/HemiphotOutput.65_final2022.csv", 
     col_types = cols(...1 = col_skip()))

head(H65.22)
#   File        CanOpen    LAI
#   <chr>         <dbl>  <dbl>
# 1 FF01_CB.jpg   0.165 Inf   
# 2 FF01_IB.jpg   0.146   3.72
# 3 FF01_OB.jpg   0.273   4.80
# 4 FF02_CB.jpg   0.225   4.41
# 5 FF02_IB.jpg   0.175   3.70
# 6 FF02_OB.jpg   0.358   3.42

hemi.21 <- H65.21 %>% filter(str_detect(File, "OB")) %>% mutate(year = "2021") 
hemi.22 <- H65.22 %>% filter(str_detect(File, "OB")) %>% mutate(year = "2022")

hemi <- full_join(hemi.21, hemi.22)

hemi$Site <- factor(gsub("_OB.jpg", "", hemi$File))
hemi$site.year <- factor(paste0(hemi$Site, "-", hemi$year)) 
hemi$year = factor(hemi$year)

dim(hemi)
summary(hemi)

### Check against the combined file compiled from last year's analysis (should be the same)

# hemi.x <- read_csv("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/Hemisphere Photos/HemipsherePhotos22_analysis/Outputs/DATE_output/Hemisphere_2021_2022_OB_CanOpen_Only.csv",       col_types = cols(...1 = col_skip())) 
# hemi.x <- hemi.x %>% mutate(year = factor(year),
#                             Site = factor(Site), 
#                             site.year = factor(site.year)) 
# dim(hemi.x)
# summary(hemi.x)
# Looks good! 


## Now combine all plots across all years 
H65.21$year <- "2021" 
H65.21$Site <- sub("_IB.jpg", "", H65.21$File)
H65.21$Site <- sub("_OB.jpg", "", H65.21$Site)
H65.21$Site <- sub("_CB.jpg", "", H65.21$Site)
H65.21$Site <- as.factor(H65.21$Site)

H65.22$year <- "2022" 
H65.22$Site <- sub("_IB.jpg", "", H65.22$File)
H65.22$Site <- sub("_OB.jpg", "", H65.22$Site)
H65.22$Site <- sub("_CB.jpg", "", H65.22$Site)
H65.22$Site <- as.factor(H65.22$Site) 


H.21 <-  H65.21 %>% mutate(
  Type = factor(case_when(
    endsWith(File, "_IB.jpg") ~ "IB",
    endsWith(File, "_OB.jpg") ~ "OB",
    endsWith(File, "_CB.jpg") ~ "CB"))) %>% 
  mutate(SitePlotYear = factor(paste0(Site, "-", Type, "-", year))) %>% 
  select(-c(year, Site, File, LAI)) 
dim(H.21)

H.22 <-  H65.22 %>% mutate(
  Type = factor(case_when(
    endsWith(File, "_IB.jpg") ~ "IB",
    endsWith(File, "_OB.jpg") ~ "OB",
    endsWith(File, "_CB.jpg") ~ "CB"))) %>% 
  mutate(SitePlotYear = factor(paste0(Site, "-", Type, "-", year))) %>% 
  select(-c(year, Site, File, LAI))  
dim(H.22)

Hdf <- full_join(H.21, H.22)
# write.csv(Hdf, "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/ForDryad/1.DataCleaning/HemispherePhotos/HemispherePhotoAnalysis_2024-01-31/AllHemisphereCanOpen.csv")
```


## Quality control and interpretation 
Plot against other measures of forest density to see how they compare

## Import forest structure measures and combine with canopy openness
```{r}
forest <- read_csv("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/ForDryad/1.DataCleaning/PrepareForestInventoryData/Output/PrepareForestInventoryData_2024-01-31/summary forest structure 2022 and 2021.csv", 
    col_types = cols(...1 = col_skip()))

open.forest <- forest %>% 
  filter(str_detect(SitePlotYear, "-OB")) %>% 
  mutate(factor(SitePlotYear)) %>% 
  mutate(VegCoverRank = case_when(
    VegCover == "Sparse" ~ 1,
    VegCover == "Intermediate" ~ 2,
    VegCover == "Intermediate, full" ~ 3,
    VegCover == "Full" ~ 4,
    VegCover == "Lush" ~ 5,
    VegCover == "Lush, full" ~ 5)) 

hemi$SitePlotYear = factor(paste0(hemi$Site, "-OB-", hemi$year))
hemi1 <- hemi %>% select(-c(site.year, Site, year, LAI)) 

open.forest1 <- left_join(open.forest, hemi1)
summary(open.forest1)

#write.csv(open.forest1, file = file.path(output_today, "OpenForestHabitats_2021_2022_forest_structure.csv")) 
#01.02.2024

forest1 <-  forest %>%  mutate(SitePlotYear = factor(SitePlotYear)) %>% 
  mutate(VegCoverRank = case_when(
    VegCover == "Sparse" ~ 1,
    VegCover == "Intermediate" ~ 2,
    VegCover == "Intermediate, full" ~ 3,
    VegCover == "Full" ~ 4,
    VegCover == "Lush" ~ 5,
    VegCover == "Lush, full" ~ 5)) %>% 
  mutate(BasalArea = BA_100) 
  
forest2 <-  left_join(Hdf, forest1)

## bring in PC1 scores 

pc <- read_csv("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/ForDryad/1.DataCleaning/PrepareForestInventoryData/Output/PrepareForestInventoryData_2024-02-01/PC1_PC2_wForestStructure_2021_2022.csv", 
     col_types = cols(...1 = col_skip()))

pc1 <- pc %>% select(SitePlotYear, PC1) %>% mutate(SitePlotYear = factor(SitePlotYear)) 

forest3 <- left_join(forest2, pc1)

```


## Describe which forest structure variables Canopy Openness is mostly highly correlated with 

### SUPPLEMENTARY MATERIALS FIGURE
#### For open sites only :
```{r}

## For open sites only : 
open.forest1$BasalArea <- open.forest1$BA_100
#  [1] "SitePlot"             "VegType"              "VegCover"             "CountSmallTrees"     
#  [5] "CountBushes"          "CountDeadTrees"       "CountLivingTrees"     "CountSnags"          
#  [9] "SumTrees"             "RelascopeSumAvg"      "PlotSize.m2"          "BA_plot"             
# [13] "BA_100"               "year"                 "SitePlotYear"         "factor(SitePlotYear)"
# [17] "File"                 "CanOpen"              "BasalArea" 

VegCoverRank <- VegCoverRank <- ggplot(
  open.forest1, aes(x = CanOpen, y = VegCoverRank)) +
  geom_point(color = "black", alpha = 0.6) +
  stat_poly_line(color = "#486266") +
  stat_poly_eq() +
  xlab("Canopy openness") +
  theme_minimal() 
VegCoverRank

CountSmallTrees <- ggplot(
  open.forest1, aes(x = CanOpen, y = CountSmallTrees)) +
  geom_point(color = "black", alpha = 0.6) +
  stat_poly_line(color = "#486266") +
  stat_poly_eq() +
  xlab("Canopy openness") +
  theme_minimal() 
CountSmallTrees

CountBushes <- ggplot(
  open.forest1, aes(x = CanOpen, y = CountBushes)) +
  geom_point(color = "black", alpha = 0.6) +
  stat_poly_line(color = "#486266") +
  stat_poly_eq() +
  xlab("Canopy openness") +
  theme_minimal() 
CountBushes

CountSnags <- ggplot(
  open.forest1, aes(x = CanOpen, y = CountSnags)) +
  geom_point(color = "black", alpha = 0.6) +
  stat_poly_line(color = "#486266") +
  stat_poly_eq() +
  xlab("Canopy openness") +
  theme_minimal() 
CountSnags

SumTrees <- ggplot(
  open.forest1, aes(x = CanOpen, y = SumTrees)) +
  geom_point(color = "black", alpha = 0.6) +
  stat_poly_line(color = "#486266") +
  stat_poly_eq() +
  xlab("Canopy openness") +
  theme_minimal() 
SumTrees

RelascopeSumAvg <- ggplot(
  open.forest1, aes(x = CanOpen, y = RelascopeSumAvg)) +
  geom_point(color = "black", alpha = 0.6) +
  stat_poly_line(color = "#486266") +
  stat_poly_eq() +
  xlab("Canopy openness") +
  theme_minimal() 
RelascopeSumAvg

BasalArea <- ggplot(
  open.forest1, aes(x = CanOpen, y = BasalArea)) +
  geom_point(color = "black", alpha = 0.6) +
  stat_poly_line(color = "#486266") +
  stat_poly_eq() +
  xlab("Canopy openness") +
  theme_minimal() 
BasalArea


plot_grid(VegCoverRank, CountBushes, CountSmallTrees, CountSnags,
          SumTrees, RelascopeSumAvg, BasalArea, ncol = 2) + theme(text = element_text(size=20)) + ggtitle ("Open habitats")
```


## Describe which forest structure variables Canopy Openness is mostly highly correlated with 

### SUPPLEMENTARY MATERIALS FIGURE
#### For all locations where we have both canopy openess and forest structure data /PC1
```{r}

pcplotopen <- ggplot(data = forest3 %>% filter(Type == "OB") %>% droplevels(), 
aes(x = PC1, y = CanOpen)) +
  geom_point(color = "black", alpha = 0.6) +
  stat_poly_line(color = "#486266") +
  stat_poly_eq() +
  ylab("Canopy openness") +
  theme_minimal() + ggtitle("Open Habitat Only") 

pcplot<- ggplot(data = forest3, aes(x = PC1, y = CanOpen)) +
  geom_point(aes(x = PC1, y = CanOpen), color = "black", alpha = 0.6) +
  stat_poly_line(color = "#486266") +
  stat_poly_eq() +
  ylab("Canopy openness") +
  theme_minimal() + ggtitle("All habitats") 

plot_grid(pcplotopen, pcplot)

## For open sites only : 
names(forest3)
#  [1] "CanOpen"          "Type"             "SitePlotYear"     "SitePlot"        
#  [5] "VegType"          "VegCover"         "CountSmallTrees"  "CountBushes"     
#  [9] "CountDeadTrees"   "CountLivingTrees" "CountSnags"       "SumTrees"        
# [13] "RelascopeSumAvg"  "PlotSize.m2"      "BA_plot"          "BA_100"          
# [17] "year"             "VegCoverRank"     "BasalArea"        "PC1" 

VegCoverRank <- VegCoverRank <- ggplot(
  forest3, aes(x = CanOpen, y = VegCoverRank)) +
  geom_point(color = "black", alpha = 0.6) +
  stat_poly_line(color = "#486266") +
  stat_poly_eq() +
  xlab("Canopy openness") +
  theme_minimal() 
VegCoverRank

CountSmallTrees <- ggplot(
  forest3, aes(x = CanOpen, y = CountSmallTrees)) +
  geom_point(color = "black", alpha = 0.6) +
  stat_poly_line(color = "#486266") +
  stat_poly_eq() +
  xlab("Canopy openness") +
  theme_minimal() 
CountSmallTrees

CountBushes <- ggplot(
  forest3, aes(x = CanOpen, y = CountBushes)) +
  geom_point(color = "black", alpha = 0.6) +
  stat_poly_line(color = "#486266") +
  stat_poly_eq() +
  xlab("Canopy openness") +
  theme_minimal() 
CountBushes

CountSnags <- ggplot(
  forest3, aes(x = CanOpen, y = CountSnags)) +
  geom_point(color = "black", alpha = 0.6) +
  stat_poly_line(color = "#486266") +
  stat_poly_eq() +
  xlab("Canopy openness") +
  theme_minimal() 
CountSnags

SumTrees <- ggplot(
  forest3, aes(x = CanOpen, y = SumTrees)) +
  geom_point(color = "black", alpha = 0.6) +
  stat_poly_line(color = "#486266") +
  stat_poly_eq() +
  xlab("Canopy openness") +
  theme_minimal() 
SumTrees

RelascopeSumAvg <- ggplot(
  forest3, aes(x = CanOpen, y = RelascopeSumAvg)) +
  geom_point(color = "black", alpha = 0.6) +
  stat_poly_line(color = "#486266") +
  stat_poly_eq() +
  xlab("Canopy openness") +
  theme_minimal() 
RelascopeSumAvg

BasalArea <- ggplot(
  forest3, aes(x = CanOpen, y = BasalArea)) +
  geom_point(color = "black", alpha = 0.6) +
  stat_poly_line(color = "#486266") +
  stat_poly_eq() +
  xlab("Canopy openness") +
  theme_minimal() 
BasalArea


plot_grid(VegCoverRank, CountBushes, CountSmallTrees, CountSnags,
          SumTrees, RelascopeSumAvg, BasalArea, ncol = 2) + theme(text = element_text(size=20)) + ggtitle ("All Habitats")
```

