---
title: "PrepareWeatherData"
output: html_document
date: "2024-01-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Goals: 

- Combine and trim all TOMST soil logger data site specific for 2021 and 2022 field seasons
- Aggregate TOMST soil logger data to night (night = 19:20 pm day 1 - 07:00 day 2)

_For more info on soil loggers, read here:_ 
_https://tomst.com/web/wp-content/uploads/2023/06/Lolly-software-Handbook.pdf_ 

- Combine with se.norge temperature and precipitation data 



### Setting up work space 
```{r}
library(data.table)
library(tidyverse)
library(beepr)
library(lubridate)
library(purrr)
library(janitor)
#renv::install("rstudio/renv")
library(renv)
library(stringr)
library(kableExtra)
library(papeR)
library(skimr)
library(vtable)
library(ggdark)
library(beepr)
library(readr)

## Setup output directory 
output <- "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/Outputs"

file.name <- "PrepareWeatherData"

todays_date <- Sys.Date()
 
dir.name <- str_c(output,"/", file.name, "_", todays_date)
dir.name
 
output_today <- dir.name
output_today

dir.create(output_today)
output_today
# "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/Outputs/PrepareWeatherData_2024-01-31"

```



## 1. Combine and trim 2021 soil logger data 
```{r}

# input_loggers <- "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/2021/Data/Soil Loggers/soil moisture TOMST Lolly data/soil moist temp time pruned to observ period/PruneToSurveyPeriod"
# 
# ################################################################################
# #### FF01 
# ################################################################################
# 
# data_94214056_0_FF01 <- read_delim("data_94214056_0_FF01.csv", 
#      delim = ";", escape_double = FALSE, col_names = FALSE, 
#      col_types = cols(`0` = col_skip(), ...10 = col_skip(), 
#          X8 = col_skip(), X9 = col_skip(), X10 = col_skip()), 
#      trim_ws = TRUE) 
# 
# data_FF01 <- as.data.frame(data_94214056_0_FF01) 
# 
# colnames(data_FF01) <- c("SerialNo", "DateTime", "TimeZone", "T1", "T2", "T3", "SoilMoisture") 
# 
# data_FF01$Site <- "FF01"
# data_FF01$datetime <- strptime(data_FF01$DateTime, 
#                                  format = "%Y.%m.%d %H:%M") 
# 
# data_FF01_2021 <- data_FF01 %>%
#                     select(-DateTime) %>% 
#                     filter(datetime > as.POSIXlt("2021.06.30 15:40", 
#                                                  format = "%Y.%m.%d %H:%M") &
#                            datetime < as.POSIXlt("2021.09.06 12:20",
#                                                  format = "%Y.%m.%d %H:%M"))
# 
# ################################################################################
# #### FF02
# ################################################################################
# 
# data_94214057_0_FF02 <- read_delim("data_94214057_0_FF02.csv", 
#      delim = ";", escape_double = FALSE, col_names = FALSE, 
#      col_types = cols(`0` = col_skip(), ...10 = col_skip(), 
#          X8 = col_skip(), X9 = col_skip(), X10 = col_skip()), 
#      trim_ws = TRUE) 
# 
# data_FF02 <- as.data.frame(data_94214057_0_FF02) 
# 
# colnames(data_FF02) <- c("SerialNo", "DateTime", "TimeZone", "T1", "T2", "T3", "SoilMoisture") 
# 
# data_FF02$Site <- "FF02"
# data_FF02$datetime <- strptime(data_FF02$DateTime, 
#                                  format = "%Y.%m.%d %H:%M") 
# 
# data_FF02_2021 <- data_FF02 %>%
#                     select(-DateTime) %>% 
#                     filter(datetime > as.POSIXlt("2021.06.30 13:40", 
#                                                  format = "%Y.%m.%d %H:%M") &
#                            datetime < as.POSIXlt("2021.08.31 12:50",
#                                                  format = "%Y.%m.%d %H:%M"))
# 
# ################################################################################
# #### FF03 
# ################################################################################
# 
# data_94214051_0_FF03 <- read_delim("data_94214051_0_FF03.csv", 
#      delim = ";", escape_double = FALSE, col_names = FALSE, 
#      col_types = cols(`0` = col_skip(), ...10 = col_skip(), 
#          X8 = col_skip(), X9 = col_skip(), X10 = col_skip()), 
#      trim_ws = TRUE) 
# 
# data_FF03 <- as.data.frame(data_94214051_0_FF03) 
# 
# colnames(data_FF03) <- c("SerialNo", "DateTime", "TimeZone", "T1", "T2", "T3", "SoilMoisture") 
# 
# data_FF03$Site <- "FF03"
# data_FF03$datetime <- strptime(data_FF03$DateTime, 
#                                  format = "%Y.%m.%d %H:%M") 
# 
# data_FF03_2021 <- data_FF03 %>%
#                     select(-DateTime) %>% 
#                     filter(datetime > as.POSIXlt("2021.06.27 17:00", 
#                                                  format = "%Y.%m.%d %H:%M") &
#                            datetime < as.POSIXlt("2021.08.30 10:50",
#                                                  format = "%Y.%m.%d %H:%M"))
# 
# ################################################################################  
# #### FF04
# ################################################################################
# 
# data_94214061_0_FF04 <- read_delim("data_94214061_0_FF04.csv", 
#      delim = ";", escape_double = FALSE, col_names = FALSE, 
#      col_types = cols(`0` = col_skip(), ...10 = col_skip(), 
#          X8 = col_skip(), X9 = col_skip(), X10 = col_skip()), 
#      trim_ws = TRUE) 
# 
# data_FF04 <- as.data.frame(data_94214061_0_FF04) 
# 
# colnames(data_FF04) <- c("SerialNo", "DateTime", "TimeZone", "T1", "T2", "T3", "SoilMoisture") 
# 
# data_FF04$Site <- "FF04"
# data_FF04$datetime <- strptime(data_FF04$DateTime, 
#                                  format = "%Y.%m.%d %H:%M") 
# 
# data_FF04_2021 <- data_FF04 %>%
#                     select(-DateTime) %>% 
#                     filter(datetime > as.POSIXlt("2021.06.27 10:30", 
#                                                  format = "%Y.%m.%d %H:%M") &
#                            datetime < as.POSIXlt("2021.08.30 12:50",
#                                                  format = "%Y.%m.%d %H:%M"))
# 
# ################################################################################  
# #### FF045
# ################################################################################
# 
# data_94214054_0_FF05 <- read_delim("data_94214054_0_FF05.csv", 
#      delim = ";", escape_double = FALSE, col_names = FALSE, 
#      col_types = cols(`0` = col_skip(), ...10 = col_skip(), 
#          X8 = col_skip(), X9 = col_skip(), X10 = col_skip()), 
#      trim_ws = TRUE) 
# 
# data_FF05 <- as.data.frame(data_94214054_0_FF05) 
# 
# colnames(data_FF05) <- c("SerialNo", "DateTime", "TimeZone", "T1", "T2", "T3", "SoilMoisture") 
# 
# data_FF05$Site <- "FF05"
# data_FF05$datetime <- strptime(data_FF05$DateTime, 
#                                  format = "%Y.%m.%d %H:%M") 
# 
# data_FF05_2021 <- data_FF05 %>%
#                     select(-DateTime) %>% 
#                     filter(datetime > as.POSIXlt("2021.06.27 11:50", 
#                                                  format = "%Y.%m.%d %H:%M") &
#                            datetime < as.POSIXlt("2021.08.31 14:30",
#                                                  format = "%Y.%m.%d %H:%M"))
# 
# ################################################################################  
# #### FF06
# ################################################################################
# data_94214053_0_FF06 <- read_delim("data_94214053_0_FF06.csv", 
#      delim = ";", escape_double = FALSE, col_names = FALSE, 
#      col_types = cols(`0` = col_skip(), ...10 = col_skip(), 
#          X8 = col_skip(), X9 = col_skip(), X10 = col_skip()), 
#      trim_ws = TRUE) 
# 
# data_FF06 <- as.data.frame(data_94214053_0_FF06) 
# 
# colnames(data_FF06) <- c("SerialNo", "DateTime", "TimeZone", "T1", "T2", "T3", "SoilMoisture") 
# 
# data_FF06$Site <- "FF06"
# data_FF06$datetime <- strptime(data_FF06$DateTime, 
#                                  format = "%Y.%m.%d %H:%M") 
# 
# data_FF06_2021 <- data_FF06 %>%
#                     select(-DateTime) %>% 
#                     filter(datetime > as.POSIXlt("2021.06.28 16:00", 
#                                                  format = "%Y.%m.%d %H:%M") &
#                            datetime < as.POSIXlt("2021.09.07 13:00",
#                                                  format = "%Y.%m.%d %H:%M"))
# 
# ################################################################################  
# #### FF07
# ################################################################################
# 
# data_94214058_0_FF07 <- read_delim("data_94214058_0_FF07.csv", 
#      delim = ";", escape_double = FALSE, col_names = FALSE, 
#      col_types = cols(`0` = col_skip(), ...10 = col_skip(), 
#          X8 = col_skip(), X9 = col_skip(), X10 = col_skip()), 
#      trim_ws = TRUE) 
# 
# data_FF07 <- as.data.frame(data_94214058_0_FF07) 
# 
# colnames(data_FF07) <- c("SerialNo", "DateTime", "TimeZone", "T1", "T2", "T3", "SoilMoisture") 
# 
# data_FF07$Site <- "FF07"
# data_FF07$datetime <- strptime(data_FF07$DateTime, 
#                                  format = "%Y.%m.%d %H:%M") 
# 
# data_FF07_2021 <- data_FF07 %>%
#                     select(-DateTime) %>% 
#                     filter(datetime > as.POSIXlt("2021.06.28 17:50", 
#                                                  format = "%Y.%m.%d %H:%M") &
#                            datetime < as.POSIXlt("2021.09.02 20:40",
#                                                  format = "%Y.%m.%d %H:%M"))
# 
# ################################################################################  
# #### FF08
# ################################################################################
# 
# data_94214060_0_FF08 <- read_delim("data_94214060_0_FF08.csv", 
#      delim = ";", escape_double = FALSE, col_names = FALSE, 
#      col_types = cols(`0` = col_skip(), ...10 = col_skip(), 
#          X8 = col_skip(), X9 = col_skip(), X10 = col_skip()), 
#      trim_ws = TRUE) 
# 
# data_FF08 <- as.data.frame(data_94214060_0_FF08) 
# 
# colnames(data_FF08) <- c("SerialNo", "DateTime", "TimeZone", "T1", "T2", "T3", "SoilMoisture") 
# 
# data_FF08$Site <- "FF08"
# data_FF08$datetime <- strptime(data_FF08$DateTime, 
#                                  format = "%Y.%m.%d %H:%M") 
# 
# data_FF08_2021 <- data_FF08 %>%
#                     select(-DateTime) %>% 
#                     filter(datetime > as.POSIXlt("2021.06.28 13:20", 
#                                                  format = "%Y.%m.%d %H:%M") &
#                            datetime < as.POSIXlt("2021.09.07 11:20",
#                                                  format = "%Y.%m.%d %H:%M"))
# 
# ################################################################################
# 
# ################################################################################  
# #### FF09
# ################################################################################
# 
# data_94214064_0_FF09 <- read_delim("data_94214064_0_FF09.csv", 
#      delim = ";", escape_double = FALSE, col_names = FALSE, 
#      col_types = cols(`0` = col_skip(), ...10 = col_skip(), 
#          X8 = col_skip(), X9 = col_skip(), X10 = col_skip()), 
#      trim_ws = TRUE) 
# 
# data_FF09 <- as.data.frame(data_94214064_0_FF09) 
# 
# colnames(data_FF09) <- c("SerialNo", "DateTime", "TimeZone", "T1", "T2", "T3", "SoilMoisture") 
# 
# data_FF09$Site <- "FF09"
# data_FF09$datetime <- strptime(data_FF09$DateTime, 
#                                  format = "%Y.%m.%d %H:%M") 
# 
# data_FF09_2021 <- data_FF09 %>%
#                     select(-DateTime) %>% 
#                     filter(datetime > as.POSIXlt("2021.06.28 14:50", 
#                                                  format = "%Y.%m.%d %H:%M") &
#                            datetime < as.POSIXlt("2021.08.30 14:50",
#                                                  format = "%Y.%m.%d %H:%M"))
# 
# ################################################################################
# 
# ################################################################################  
# #### FF10
# ################################################################################
# 
# data_94214059_0_FF10 <- read_delim("data_94214059_0_FF10.csv", 
#      delim = ";", escape_double = FALSE, col_names = FALSE, 
#      col_types = cols(`0` = col_skip(), ...10 = col_skip(), 
#          X8 = col_skip(), X9 = col_skip(), X10 = col_skip()), 
#      trim_ws = TRUE) 
# 
# data_FF10 <- as.data.frame(data_94214059_0_FF10) 
# 
# colnames(data_FF10) <- c("SerialNo", "DateTime", "TimeZone", "T1", "T2", "T3", "SoilMoisture") 
# 
# data_FF10$Site <- "FF10"
# data_FF10$datetime <- strptime(data_FF10$DateTime, 
#                                  format = "%Y.%m.%d %H:%M") 
# 
# data_FF10_2021 <- data_FF10 %>%
#                     select(-DateTime) %>% 
#                     filter(datetime > as.POSIXlt("2021.06.27 18:40", 
#                                                  format = "%Y.%m.%d %H:%M") &
#                            datetime < as.POSIXlt("2021.08.31 11:00",
#                                                  format = "%Y.%m.%d %H:%M"))
# 
# ################################################################################
# 
# ################################################################################  
# #### FF11
# ################################################################################
# 
# data_94214065_0_FF11 <- read_delim("data_94214065_0_FF11.csv", 
#      delim = ";", escape_double = FALSE, col_names = FALSE, 
#      col_types = cols(`0` = col_skip(), ...10 = col_skip(), 
#          X8 = col_skip(), X9 = col_skip(), X10 = col_skip()), 
#      trim_ws = TRUE) 
# 
# data_FF11 <- as.data.frame(data_94214065_0_FF11) 
# 
# colnames(data_FF11) <- c("SerialNo", "DateTime", "TimeZone", "T1", "T2", "T3", "SoilMoisture") 
# 
# data_FF11$Site <- "FF11"
# data_FF11$datetime <- strptime(data_FF11$DateTime, 
#                                  format = "%Y.%m.%d %H:%M") 
# 
# data_FF11_2021 <- data_FF11 %>%
#                     select(-DateTime) %>% 
#                     filter(datetime > as.POSIXlt("2021.06.30 14:30", 
#                                                  format = "%Y.%m.%d %H:%M") &
#                            datetime < as.POSIXlt("2021.09.06 11:14",
#                                                  format = "%Y.%m.%d %H:%M"))
# 
# 
# ################################################################################  
# #### FF12
# ################################################################################
# 
# data_94214052_0_FF12 <- read_delim("data_94214052_0_FF12.csv", 
#      delim = ";", escape_double = FALSE, col_names = FALSE, 
#      col_types = cols(`0` = col_skip(), ...10 = col_skip(), 
#          X8 = col_skip(), X9 = col_skip(), X10 = col_skip()), 
#      trim_ws = TRUE) 
# 
# data_FF12 <- as.data.frame(data_94214052_0_FF12) 
# 
# colnames(data_FF12) <- c("SerialNo", "DateTime", "TimeZone", "T1", "T2", "T3", "SoilMoisture") 
# 
# data_FF12$Site <- "FF12"
# data_FF12$datetime <- strptime(data_FF12$DateTime, 
#                                  format = "%Y.%m.%d %H:%M") 
# 
# data_FF12_2021 <- data_FF12 %>%
#                     select(-DateTime) %>% 
#                     filter(datetime > as.POSIXlt("2021.06.27 15:00", 
#                                                  format = "%Y.%m.%d %H:%M") &
#                            datetime < as.POSIXlt("2021.09.02 22:50",
#                                                  format = "%Y.%m.%d %H:%M"))
# 
# ################################################################################
# pruned_loggers_2021_list <- list(data_FF01_2021, data_FF02_2021, data_FF03_2021,
#                               data_FF04_2021, data_FF05_2021, data_FF06_2021,
#                               data_FF07_2021, data_FF08_2021, data_FF09_2021,
#                               data_FF10_2021, data_FF11_2021, data_FF12_2021)
# 
# do.call("rbind", listOfDataFrames)
# big_loggers_21 <- do.call("rbind", pruned_loggers_2021_list)
# log21df <- big_loggers_21 %>% mutate(Site = factor(Site))
# summary(log21df$Site)


# dir.create("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/2021/Data/Soil Loggers/soil moisture TOMST Lolly data/soil moist temp time pruned to observ period/PruneToSurveyPeriod/outputs")
# 
# write.csv(log21df, "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/2021/Data/Soil Loggers/soil moisture TOMST Lolly data/soil moist temp time pruned to observ period/PruneToSurveyPeriod/outputs/raw_loggerdata_combined.csv") 

## Need to fix the timezone on this dataset 

log21 <- read_csv("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/ForDryad/1.DataCleaning/PrepareWeatherData/raw_loggerdata_combined_FF2021.csv", 
     col_types = cols(...1 = col_skip()))
dim(log21)
## 110858 obs of 8 vars 

## Fix timezone
tz(log21$datetime) # "UTC" 
log21$datetime <- force_tz(log21$datetime, tzone = "Europe/Berlin")
tz(log21$datetime) # "Europe/Berlin"
log21df <- log21 %>% select(-c(TimeZone, SerialNo))

```


## 2022 soil logger data - already combined and trimmed
```{r}

log22df <- read_csv("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/ForDryad/1.DataCleaning/PrepareWeatherData/FolloForest2022_SoilMoistureData_RawReads_AllSites.csv", 
     col_types = cols(...1 = col_skip(), Easting = col_skip(), 
         Northing = col_skip()))
dim(log22df)
# 197272      6

log22df <- log22df %>% 
  rename(SoilMoisture = PercVol) %>% 
  select(-c(n_site_reading, Hu)) %>% 
  mutate(Site = factor(Site))

tz(log22df$datetime) # UTC
log22df$datetime <- force_tz(log22df$datetime, tzone = "Europe/Berlin")
tz(log22df$datetime) # "Europe/Berlin"

```


## Merge soil logger data and then make night aggregated 
```{r}
logdf <- full_join(log21df, log22df)
summary(logdf)

summary(logdf$Site) 
# 308130 obs

# Only keep values between 17:00 - 00:00 and 00:00-08:00
logdf1 <- logdf %>% mutate(time = format(as.POSIXct(datetime), format = "%H:%M:%S")) 
logdf1$time <- lubridate::hms(logdf1$time)
logdf1$hour <- hour(logdf1$time) 
logdf2 <- logdf1 %>% filter(hour < 9 | hour > 16) 
dim(logdf2)
# 205592      8

# Check that this worked 
hist(logdf2$hour)
hist(logdf1$hour)

## Now create an HOUR.12 column 
logdf2$nighttime <- logdf2$datetime - 12*60*60
logdf2$time.12 <- lubridate::hms(format(as.POSIXct(logdf2$nighttime), format = "%H:%M:%S"))
logdf2$hour.12 <- hour(logdf2$time.12)
logdf2$night <- as.Date(logdf2$nighttime)

# tz(logdf2$datetime)
# "Europe/Berlin"
# tz(logdf2$nighttime)
# "Europe/Berlin"

dim(logdf2)
# 205592     12 vars 

## Aggregate to night 
log.n <- logdf2 %>% group_by(night, Site) %>% 
  dplyr::summarize(T1 = mean(T1),
                   T2 = mean(T2), 
                   T3 = mean(T3), 
                   SoilMoisture = mean(SoilMoisture)) 
summary(log.n)
summary(logdf2)
dim(log.n)
# 2167 obs 12 vars 

# write.csv(log.n, file = file.path(output_today, "AllSoilMoistureData__2021_2022_aggregate_night.csv")) 
# 11.01.2024

```


## Prepare se.norge temperature data 
```{r}

FF01_temp <- read_delim("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/weather data seNorge/seNorge precipitation and temperature/SeNorge temp downloaded 11-12-2023/FF01 temp.csv", 
     delim = ";", escape_double = FALSE, trim_ws = TRUE, 
     skip = 1)
FF01_temp$Site <- "FF01"

FF02_temp <- read_delim("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/weather data seNorge/seNorge precipitation and temperature/SeNorge temp downloaded 11-12-2023/FF02 temp.csv", 
     delim = ";", escape_double = FALSE, trim_ws = TRUE, 
     skip = 1)
FF02_temp$Site <- "FF02"

FF03_temp <- read_delim("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/weather data seNorge/seNorge precipitation and temperature/SeNorge temp downloaded 11-12-2023/FF03 temp.csv", 
     delim = ";", escape_double = FALSE, trim_ws = TRUE, 
     skip = 1)
FF03_temp$Site <- "FF03"

FF04_temp <- read_delim("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/weather data seNorge/seNorge precipitation and temperature/SeNorge temp downloaded 11-12-2023/FF04 temp.csv", 
     delim = ";", escape_double = FALSE, trim_ws = TRUE, 
     skip = 1)
FF04_temp$Site <- "FF04"

FF05_temp <- read_delim("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/weather data seNorge/seNorge precipitation and temperature/SeNorge temp downloaded 11-12-2023/FF05 temp.csv", 
     delim = ";", escape_double = FALSE, trim_ws = TRUE, 
     skip = 1)
FF05_temp$Site <- "FF05"

FF06_temp <- read_delim("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/weather data seNorge/seNorge precipitation and temperature/SeNorge temp downloaded 11-12-2023/FF06 temp.csv", 
     delim = ";", escape_double = FALSE, trim_ws = TRUE, 
     skip = 1)
FF06_temp$Site <- "FF06"

FF07_temp <- read_delim("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/weather data seNorge/seNorge precipitation and temperature/SeNorge temp downloaded 11-12-2023/FF07 temp.csv", 
     delim = ";", escape_double = FALSE, trim_ws = TRUE, 
     skip = 1)
FF07_temp$Site <- "FF07"

FF08_temp <- read_delim("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/weather data seNorge/seNorge precipitation and temperature/SeNorge temp downloaded 11-12-2023/FF08 temp.csv", 
     delim = ";", escape_double = FALSE, trim_ws = TRUE, 
     skip = 1)
FF08_temp$Site <- "FF08"

FF09_temp <- read_delim("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/weather data seNorge/seNorge precipitation and temperature/SeNorge temp downloaded 11-12-2023/FF09 temp.csv", 
     delim = ";", escape_double = FALSE, trim_ws = TRUE, 
     skip = 1)
FF09_temp$Site <- "FF09"

FF10_temp <- read_delim("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/weather data seNorge/seNorge precipitation and temperature/SeNorge temp downloaded 11-12-2023/FF10 temp.csv", 
     delim = ";", escape_double = FALSE, trim_ws = TRUE, 
     skip = 1)
FF10_temp$Site <- "FF10"

FF11_temp <- read_delim("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/weather data seNorge/seNorge precipitation and temperature/SeNorge temp downloaded 11-12-2023/FF11 temp.csv", 
     delim = ";", escape_double = FALSE, trim_ws = TRUE, 
     skip = 1)
FF11_temp$Site <- "FF11"

FF12_temp <- read_delim("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/weather data seNorge/seNorge precipitation and temperature/SeNorge temp downloaded 11-12-2023/FF12 temp.csv", 
     delim = ";", escape_double = FALSE, trim_ws = TRUE, 
     skip = 1) 
FF12_temp$Site <- "FF12"

temp.list <- list(FF01_temp, FF02_temp, FF03_temp, 
                  FF04_temp, FF05_temp, FF06_temp, 
                  FF07_temp, FF08_temp, FF09_temp, 
                  FF10_temp, FF11_temp, FF12_temp)

bigtemp<- rbindlist(temp.list, fill = TRUE)
bigtemp$datetime <- as.POSIXct(bigtemp$Date, format ="%d.%m.%Y %H:%M")
tz(bigtemp$datetime) <- "Europe/Berlin"
bigtemp$night <- as.Date(bigtemp$datetime)
bigtemp$temperature <- bigtemp[,2]

bigtemp21 <- bigtemp %>% dplyr::filter(between(
  night, as.Date("2021-05-14", format = "%Y-%m-%d"), as.Date("2021-09-14"))) 

ggplot(bigtemp21) + geom_smooth(aes(x = night, y = temperature)) + facet_wrap(~Site)

bigtemp22 <- bigtemp %>% dplyr::filter(between(
  night, as.Date("2022-05-04", format = "%Y-%m-%d"), as.Date("2022-09-21"))) %>% filter(Site != "FF12")

ggplot(bigtemp22) + geom_smooth(aes(x = night, y = temperature)) + facet_wrap(~Site)

bigtempdf <- full_join(bigtemp21, bigtemp22) # 3038
names(bigtempdf)
bigtempdf1 <- bigtempdf %>% select(Site, datetime, temperature, night) 
tz(bigtempdf1$datetime) # Europe/Berlin - good! 
# 3039 obs of 4 vars 

```


## Prepare se.norge precipitation data 
```{r}
FF01_precip <- read_delim("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/weather data seNorge/seNorge precipitation and temperature/seNorge precipitation downloaded 11-12-2023/FF01 precip.csv", 
     delim = ",", escape_double = FALSE, trim_ws = TRUE)
FF01_precip$Site <- "FF01"

FF02_precip <- read_delim("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/weather data seNorge/seNorge precipitation and temperature/seNorge precipitation downloaded 11-12-2023/FF02 precip.csv", 
     delim = ",", escape_double = FALSE, trim_ws = TRUE)
FF02_precip$Site <- "FF02"

FF03_precip <- read_delim("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/weather data seNorge/seNorge precipitation and temperature/seNorge precipitation downloaded 11-12-2023/FF03 precip.csv", 
     delim = ",", escape_double = FALSE, trim_ws = TRUE)
FF03_precip$Site <- "FF03"

FF04_precip <- read_delim("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/weather data seNorge/seNorge precipitation and temperature/seNorge precipitation downloaded 11-12-2023/FF04 precip.csv", 
     delim = ",", escape_double = FALSE, trim_ws = TRUE)
FF04_precip$Site <- "FF04"

FF05_precip <- read_delim("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/weather data seNorge/seNorge precipitation and temperature/seNorge precipitation downloaded 11-12-2023/FF05 precip.csv", 
     delim = ",", escape_double = FALSE, trim_ws = TRUE)
FF05_precip$Site <- "FF05"

FF06_precip <- read_delim("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/weather data seNorge/seNorge precipitation and temperature/seNorge precipitation downloaded 11-12-2023/FF06 precip.csv", 
     delim = ",", escape_double = FALSE, trim_ws = TRUE)
FF06_precip$Site <- "FF06"

FF07_precip <- read_delim("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/weather data seNorge/seNorge precipitation and temperature/seNorge precipitation downloaded 11-12-2023/FF07 precip.csv", 
     delim = ",", escape_double = FALSE, trim_ws = TRUE)
FF07_precip$Site <- "FF07"

FF08_precip <- read_delim("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/weather data seNorge/seNorge precipitation and temperature/seNorge precipitation downloaded 11-12-2023/FF08 precip.csv", 
     delim = ",", escape_double = FALSE, trim_ws = TRUE)
FF08_precip$Site <- "FF08"

FF09_precip <- read_delim("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/weather data seNorge/seNorge precipitation and temperature/seNorge precipitation downloaded 11-12-2023/FF09 precip.csv", 
     delim = ",", escape_double = FALSE, trim_ws = TRUE)
FF09_precip$Site <- "FF09"

FF10_precip <- read_delim("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/weather data seNorge/seNorge precipitation and temperature/seNorge precipitation downloaded 11-12-2023/FF10 precip.csv", 
     delim = ",", escape_double = FALSE, trim_ws = TRUE)
FF10_precip$Site <- "FF10"

FF11_precip <- read_delim("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/weather data seNorge/seNorge precipitation and temperature/seNorge precipitation downloaded 11-12-2023/FF11 precip.csv", 
     delim = ",", escape_double = FALSE, trim_ws = TRUE)
FF11_precip$Site <- "FF11"

FF12_precip <- read_delim("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/weather data seNorge/seNorge precipitation and temperature/seNorge precipitation downloaded 11-12-2023/FF12 precip.csv", 
     delim = ",", escape_double = FALSE, trim_ws = TRUE) 
FF12_precip$Site <- "FF12"

precip.list <- list(FF01_precip, FF02_precip, FF03_precip, 
                  FF04_precip, FF05_precip, FF06_precip, 
                  FF07_precip, FF08_precip, FF09_precip, 
                  FF10_precip, FF11_precip, FF12_precip)

bigprecip<- rbindlist(precip.list, fill = TRUE)
bigprecip$datetime <- as.POSIXct(bigprecip$Date, format ="%d.%m.%Y %H:%M")
tz(bigprecip$datetime) <- "Europe/Berlin"
bigprecip$night <- as.Date(bigprecip$datetime)
bigprecip$rainfall <- bigprecip[,2]

bigprecip21 <- bigprecip %>% dplyr::filter(between(
  night, as.Date("2021-05-14", format = "%Y-%m-%d"), as.Date("2021-09-14"))) 

ggplot(bigprecip21) + geom_smooth(aes(x = night, y = rainfall)) + facet_wrap(~Site)

bigprecip22 <- bigprecip %>% dplyr::filter(between(
  night, as.Date("2022-05-04", format = "%Y-%m-%d"), as.Date("2022-09-21"))) %>% filter(Site != "FF12")

ggplot(bigprecip22) + geom_smooth(aes(x = night, y = rainfall)) + facet_wrap(~Site)

bigprecipdf <- full_join(bigprecip21, bigprecip22) # 3180
names(bigprecipdf)
bigprecipdf1 <- bigprecipdf %>% select(Site, datetime, rainfall, night) 
dim(bigprecipdf1)
# 3039 obs of 4 vars 
tz(bigprecipdf1$datetime) # "Europe/Berlin", good! 

```


## Combine se.norge datasets as well as tomst data 
```{r}
weather1 <- left_join(bigtempdf1, bigprecipdf1) 
dim(weather1)
names(weather1)
weather1$Site <- factor(weather1$Site)
tz(weather1$datetime)
# 3039    5
#"Site"        "datetime"    "temperature" "night"       "rainfall"   

#write.csv(weather1, file = file.path(output_today, "se.norge_precip_temp_combined_2021_2022.csv"))

names(log.n)
# "night"        "Site"         "T1"           "T2"           "T3"           "SoilMoisture"

# Already checked both in Europe/Berlin TZ

weather2 <- left_join(log.n, weather1)
summary(weather2)
dim(weather2)
# 2168    9

# Create site average moisture column 
moist.site <- log.n %>% 
  mutate(year = year(night),
         site.year = factor(paste0(Site, "-", year))) %>% 
  group_by(site.year) %>% dplyr::summarize(moist.site = mean(SoilMoisture))

weather2$year <- year(weather2$night)
weather2$site.year <- factor(paste0(weather2$Site, "-", weather2$year)) 
  
weather3 <- left_join(weather2, moist.site)
summary(weather3)
dim(weather3)
# 2168   12
names(weather3)
 # [1] "night"        "Site"         "T1"           "T2"           "T3"           "SoilMoisture"
 # [7] "datetime"     "temperature"  "rainfall"     "year"         "site.year"    "moist.site"

#write.csv(weather3, file = file.path(output_today, "se.norge_precip_temp_combined_TOMST4_2021_2022.csv"))

```

