---
title: "NightAggregateBats_DensityManuscript"
output: html_document
date: "2024-02-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Goals: 
- Aggregate bat data to night
- Insert zero nights when detectors were active but did not record bat activity
- Compile covariates 


```{r}

library(data.table)
library(tidyverse)
library(beepr)
library(lubridate)
library(purrr)
library(janitor)
#renv::install("rstudio/renv")
library(renv)
library(stringr)
library(beepr)
library(kableExtra)
library(papeR)
library(skimr)
library(vtable)
library(ggdark)
library(RColorBrewer)
library(cowplot)
library(readxl)
library(readr)

## Setup output directory 
output <- "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/ForDryad/2.AggregationCombineCovariates/NightAggregateBats_DensityManuscript/Outputs"

file.name <- "NightAggBats"

todays_date <- Sys.Date()
 
dir.name <- str_c(output,"/", file.name, "_", todays_date)
dir.name
 
output_today <- dir.name
output_today

dir.create(output_today)
output_today
## "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/ForDryad/2.AggregationCombineCovariates/NightAggregateBats_DensityManuscript/Outputs/NightAggBats_2024-02-01"

```

## Import datasets
```{r}

## Nightly aggregated for all manual acoustic analysis 
bats <- read_csv("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/ForDryad/2.AggregationCombineCovariates/NightAggregateBats_DensityManuscript/Inputs/ManualAnalaysis21_22_combined_datetime_PlotType_Guild.csv",
     col_types = cols(...1 = col_skip()))
dim(bats)
# 108989     22

## Nights when detectors were working but no data selected manually added
active.nights <- read_csv("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/ForDryad/2.AggregationCombineCovariates/NightAggregateBats_DensityManuscript/Inputs/active_detector.nights_2021_2022.csv", 
     col_types = cols(...1 = col_skip()))
# 8155 obs of 4 vars

## Forest structure data
forest <-  read_csv("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/ForDryad/2.AggregationCombineCovariates/NightAggregateBats_DensityManuscript/Inputs/PC1_PC2_wForestStructure_2021_2022.csv", 
     col_types = cols(...1 = col_skip()))
forest$SitePlotYear <- factor(forest$SitePlotYear)
# 69 obs of 10 vars

## Day length 
photo <- read_csv("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/ForDryad/2.AggregationCombineCovariates/NightAggregateBats_DensityManuscript/Inputs/daylength.csv", 
      col_types = cols(...1 = col_skip()))

# weather data aggregated with TOMST data loggers 
weather.log <- read_csv("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/ForDryad/2.AggregationCombineCovariates/NightAggregateBats_DensityManuscript/Inputs/se.norge_precip_temp_combined_TOMST4_2021_2022.csv", 
     col_types = cols(...1 = col_skip()))

weather.log <- weather.log %>% mutate(
  Site = factor(Site), 
  year = factor(year),
  site.year = factor(site.year)) %>% select(-datetime)
# 2167 obs 11 vars

# weather data aggregated with se.norge data 
weather.se <- read_csv("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/ForDryad/2.AggregationCombineCovariates/NightAggregateBats_DensityManuscript/Inputs/se.norge_precip_temp_combined_2021_2022.csv", 
     col_types = cols(...1 = col_skip()))

weather.se <- weather.se %>% dplyr::mutate(
  Site = factor(Site), 
  year = factor(year(night)),
  site.year = factor(paste0(Site, "-", year))) %>% select(-datetime)
#3039 obs 6 vars

## Hemisphere photos 
hemi <- read_csv("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/ForDryad/2.AggregationCombineCovariates/NightAggregateBats_DensityManuscript/Inputs/AllHemisphereCanOpen.csv", 
     col_types = cols(...1 = col_skip()))
# 57 obs 3 vars 
hemi$SitePlotYear <- factor(hemi$SitePlotYear) 
```



## House keeping
```{r}
bats1 <- bats %>% 
  mutate(manual.id = factor(manual.id),
         behavior = factor(behavior), 
         guild = factor(guild), 
         year = factor(year), 
         Detector = factor(Detector), 
         detector.year = factor(detector.year),
         SitePlot = factor(SitePlot),
         PlotType = factor(PlotType),
         Site = factor(Site),
         night = DATE.12) %>% 
  mutate(SitePlotYear = factor(paste0(SitePlot, "-", year))) %>% 
  filter(guild != "Noise") %>% droplevels() 
# 106525 (2464 noise files dropped)


tz(bats1$datetime) # "UTC"
tz(bats1$nighttime) # "UTC" 

bats1$datetime <- force_tz(bats1$datetime, tzone = "Europe/Berlin")
bats1$nighttime <- force_tz(bats1$nighttime, tzone = "Europe/Berlin")
tz(bats1$datetime) # "Europe/Berlin"
tz(bats1$nighttime) # "Europe/Berlin" 
# Good 


active.nights$SitePlot <- gsub("FF1-", "FF01-", active.nights$SitePlot)
active.nights$SitePlot <- gsub("FF2-", "FF02-", active.nights$SitePlot)
active.nights$SitePlot <- gsub("FF3-", "FF03-", active.nights$SitePlot)
active.nights$SitePlot <- gsub("FF4-", "FF04-", active.nights$SitePlot)
active.nights$SitePlot <- gsub("FF5-", "FF05-", active.nights$SitePlot)
active.nights$SitePlot <- gsub("FF6-", "FF06-", active.nights$SitePlot)
active.nights$SitePlot <- gsub("FF7-", "FF07-", active.nights$SitePlot)
active.nights$SitePlot <- gsub("FF8-", "FF08-", active.nights$SitePlot)
active.nights$SitePlot <- gsub("FF9-", "FF09-", active.nights$SitePlot)

active.nights$SitePlot <- factor(active.nights$SitePlot)

active.nights$SitePlotYear <- factor(paste0(active.nights$SitePlot, "-", active.nights$year)) 

test <- active.nights %>% mutate(test = paste0(SitePlotYear, "-", night)) 
test1 <- test$test
test2  <- test1[duplicated(test1)]
test2 # No duplicates! 

active.nights.21 <- active.nights %>% filter(year == "2021") %>% droplevels()
# 3808 detector nights in 2021 

active.nights.22 <- active.nights %>% filter(year == "2022") %>% droplevels()
# 4347 detector nights in 2022

```


#####################################
## Insert the zero nights ## *3 behaviors*
#####################################

```{r}
summary(bats1$behavior)
#      Both Commuting   Feeding    Social 
#      148     83151     15342      7884 


# Given how few bat passes have both feeding and social activity, I am going to merge down to three behavior levels and re-aggregate

# Create new behavior column 
batsx <- bats1 %>% mutate(behavior1 = case_when(
  behavior == "Commuting" ~ "Commuting", 
  behavior == "Social" ~ "Social", 
  behavior == "Feeding" ~ "Feeding", 
  behavior == "Both" ~ "Feeding"
)) %>% mutate(behavior1 = factor(behavior1))

summary(batsx$behavior1)
# Commuting   Feeding    Social 
#     83151     15490      7884 

###########################################
#### Insert zeroes for each year separately. 
        ######### 2021 #########
###########################################

bats_21 <- batsx %>% dplyr::filter(year == "2021") %>% droplevels()
#48866 bat passes 

batmap <- bats_21 %>% dplyr::select(Site, SitePlot, SitePlotYear, PlotType) %>% unique()

timemap <- bats_21 %>% dplyr::select(night) %>% distinct(night, .keep_all = TRUE) 
# 121 nights of survey (before adding in zero nights)

### AGGREGATE TO N BAT PASSES PER MANUAL ID PER BEHAVIOR PER NIGHT
# Number of bat passes per night for each manual ID AND behavior summed 
bats2 <- bats_21 %>% group_by(SitePlotYear, night, manual.id, behavior1) %>% dplyr::summarize(batpass = sum(n()))
# 11106 obs of 5 vars
head(bats2)

bats3 <- left_join(bats2, batmap)
summary(bats3) # 11106 detector-manual.id-behavior nights  

dat <- bats3 
dim(dat) # 11106     9
levels(dat$SitePlotYear)

active.nights <- active.nights.21 %>% distinct() #3805 detector nights 
dim(active.nights)
# 3805    5
# 3805 - 3784 ...21 nights difference

summary(active.nights$SitePlotYear)
head(active.nights)

night <- unique(active.nights$night)
# 124 unique nights  

temp<-expand.grid(SitePlotYear= unique(dat$SitePlotYear),  
                  night = unique(active.nights$night), 
                  manual.id = unique(dat$manual.id), 
                  behavior1 = unique(dat$behavior1)) 
dim(temp)
levels(temp$SitePlotYear)
summary(temp)
dim(temp)
#133920        4

temp$night <-  as.Date(temp$night, format = "%Y-%m-%d")
active.nights$night <-  as.Date(active.nights$night, format = "%Y-%m-%d")

active.nights$SitePlotYear <- as.factor(active.nights$SitePlotYear)

str(temp)
str(active.nights)

temp2<-merge(temp,active.nights)
levels(temp2$SitePlotYear)
dim(temp2)
# 114240  obs 

temp3<-merge(temp2, dat, all.x=TRUE) 
dim(temp3) # 114240          10
levels(temp3$SitePlotYear)

temp3$active.night <- as.factor(temp3$active.night) # 

summary(temp3$SitePlotYear)
summary(temp3) # 103134 zeros introduced 

# reformat factor columns and then replace NA bat passes with zeros 
nbats <- temp3 %>% 
  dplyr::select(-c(Site, active.night, year, SitePlot, PlotType)) %>% 
  droplevels() 

nbats1 <- left_join(nbats, batmap, by = "SitePlotYear")
summary(nbats1)
dim(nbats1)
# 114240            8

# replace NAs with zeros 
nbats1[is.na(nbats1)] <- 0 
summary(nbats1)

levels(nbats1$SitePlotYear)



FF12CB2021 <- nbats1 %>% filter(SitePlotYear == "FF12-CB-2021") %>% droplevels()

ggplot(FF12CB2021) + 
  geom_count(aes(x = night, y = batpass, color = manual.id, shape = behavior1) ) 

### Visualize to check rather or not this worked #### 

nbats1 %>% filter(batpass > 0) %>% 
  ggplot(aes(x = night, y = batpass)) + 
  geom_point(alpha = 0.3) + facet_wrap(~SitePlot) + ylim(c(1,50))

### Now check that the suvey effort is covered properly 
# surveyeffort <- ggplot(nbats1) + 
#   geom_point(aes(x = night, y = Site), 
#              color = "#DAB82A", shape = 19,  alpha = 0.5) +  
#   facet_wrap(~PlotType, nrow=3) + 
#   xlab("2021") + ylab(" ") +
#   ggtitle("Survey effort") + 
#   theme(legend.position="none") +
#   theme(panel.grid.major = element_blank(), 
#         panel.grid.minor = element_blank(),
#         panel.background = element_blank(), 
#         text = element_text(size = 12),
#         axis.line = element_line(colour = "black"))
# surveyeffort

# Remnove 02.09.2021 data for FF7 and FF12 sites - detectors did not complete full night of recording. Were retrieved during night time. 

# should lose 240 obs total. 
dropthese <- nbats1 %>% # 
  subset(night == "2021-09-02" & Site %in% c('FF07', 'FF12'))%>% 
  droplevels()

sum(dropthese$batpass)
# 6 bat passes dropped on incomplete nights. 

nbats2 <- anti_join(nbats1, dropthese)

nbats_2021 <- nbats2
# 114060
sum(nbats_2021$batpass)
# 48860

dim(bats_21)
# 48866    25
# 6 bat pass difference only

###########################################
#### Insert zeroes for each year separately. 
        ######### 2022 #########
###########################################
bats_22 <- batsx %>% filter(year == "2022") %>% droplevels()
#57659 bat passes 

batmap <- bats_22 %>% dplyr::select(Site, SitePlot, SitePlotYear, PlotType) %>% unique()

timemap <- bats_22 %>% dplyr::select(night) %>% distinct(night, .keep_all = TRUE) # 140 nights of survey (before adding in zero nights)

### AGGREGATE TO N BAT PASSES PER MANUAL ID PER BEHAVIOR PER NIGHT
# Number of bat passes per night for each manual ID AND behavior summed 
bats2 <- bats_22 %>% dplyr::group_by(SitePlotYear, night, manual.id, behavior1) %>% dplyr::summarize(batpass = sum(n()))
# 12973      obs of 5 vars
head(bats2)

bats3 <- dplyr::left_join(bats2, batmap)
summary(bats3) # 12973      detector-manual.id-behavior nights  

dat <- bats3 
dim(dat) # 12973          7
levels(dat$SitePlotYear)

active.nights <- active.nights.22 %>% distinct() #4347 detector nights 
summary(active.nights$SitePlotYear)
head(active.nights)

night <- unique(active.nights$night)
# 140 nights, no unique dates added to the season 

temp<-expand.grid(SitePlotYear= unique(dat$SitePlotYear),  
                  night = unique(active.nights$night), 
                  manual.id = unique(dat$manual.id), 
                  behavior1 = unique(dat$behavior1)) 
dim(temp)
levels(temp$SitePlotYear)
summary(temp)
# 113400            4

temp$night <-  as.Date(temp$night, format = "%Y-%m-%d")
active.nights$night <-  as.Date(active.nights$night, format = "%Y-%m-%d")

active.nights$SitePlotYear <- as.factor(active.nights$SitePlotYear)

str(temp)
str(active.nights)

temp2<-merge(temp,active.nights)
levels(temp2$SitePlotYear)
dim(temp2)
#130410             obs 

temp3<-merge(temp2, dat, all.x=TRUE) 
dim(temp3) # 130080         9
levels(temp3$SitePlotYear)

temp3$active.night <- as.factor(temp3$active.night) # 

summary(temp3$SitePlotYear)
summary(temp3) # 117437        zeros introduced 

# reformat factor columns and then replace NA bat passes with zeros 
nbats <- temp3 %>% 
  dplyr::select(-c(Site, active.night, year, SitePlot, PlotType)) %>% 
  droplevels() 

nbats1 <- left_join(nbats, batmap, by = "SitePlotYear")
summary(nbats1)
dim(nbats1)
# 130410          8

# replace NAs with zeros 
nbats1[is.na(nbats1)] <- 0 
summary(nbats1)

levels(nbats1$SitePlotYear)


# ggplot(nbats1) + geom_count(aes(x = night, y = batpass, color = manual.id, shape = behavior1)) 

### Visualize to check rather or not this worked #### 
nbats1 %>% filter(batpass > 0) %>% 
  ggplot(aes(x = night, y = batpass)) + 
  geom_point(alpha = 0.3) + facet_wrap(~SitePlot) + ylim(c(1,50))

nbats1 %>% ggplot(aes(x = SitePlot, y = batpass, fill = behavior1)) + geom_bar(stat = "identity") + facet_wrap(~manual.id) + ylim(c(0,200))

nbats_2022 <- nbats1
# 130410

### Now check that the survey effort is covered properly 
# surveyeffort <- ggplot(nbats1) + 
#   geom_point(aes(x = night, y = Site), 
#              color = "#DAB82A", shape = 19,  alpha = 0.5) +  
#   facet_wrap(~PlotType, nrow=3) + 
#   xlab("2022") + ylab(" ") +
#   ggtitle("Survey effort") + 
#   theme(legend.position="none") +
#   theme(panel.grid.major = element_blank(), 
#         panel.grid.minor = element_blank(),
#         panel.background = element_blank(), 
#         text = element_text(size = 12),
#         axis.line = element_line(colour = "black"))
# surveyeffort

```


###########################################
#### combine years and add back metadata
###########################################


```{r}
###########################################
#### combine years and add back metadata
###########################################
dim(nbats_2021)
# 114060      8                  
dim(nbats_2022)
# 130410      8            

# 130410 + 114060 = 244470     
batsdf <- full_join(nbats_2021, nbats_2022)
dim(batsdf) # 244470      8 - nice!! 
names(batsdf)
batsdf <- batsdf %>% rename(behavior = behavior1)
names(batsdf)

# reconnect the metadata 
names(bats1)
batsx1 <- batsx %>% dplyr::select(-behavior) %>%  rename(behavior = behavior1)

meta <- batsx1 %>% dplyr::select(SitePlotYear, PlotType, Detector) %>% unique()
meta1 <- batsx1 %>% dplyr::select(manual.id, guild) %>% unique()

batsdf1 <- left_join(batsdf, meta)
batsdf2 <- left_join(batsdf1, meta1)

summary(batsdf2)
dim(batsdf2)
# 244470     10
sum(batsdf2$batpass)
# 106519

# write.csv(batsdf2, "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/ForDryad/2.AggregationCombineCovariates/NightAggregateBats_DensityManuscript/Outputs/NightAggregateBats_DensityManuscript_2024-02-01/DensityBats.csv")
#  01.02.2024

```

## Combine Night aggregated bat data with forest structure, photoperiod and and weather data 

```{r}

#Combine bats with forest 
batsdf3 <- left_join(batsdf2, forest)
head(batsdf3)
summary(batsdf3)
dim(batsdf3)
# 244470     19

## Combine with day length 
batsdf4 <- left_join(batsdf3, photo) %>% select(-c(lat, lon))
summary(batsdf4)
dim(batsdf4)
# 244470     26

## Combine with se. norge weather data 
batsdf5 <- left_join(batsdf4, weather.se) %>% select(-site.year)
summary(batsdf5)
dim(batsdf5)
# 244470     29
sum(batsdf5$batpass)
# 106519

## What is the percent of zero observations? 
sum(batsdf$batpass == 0)/nrow(batsdf) * 100 
# 90.15217

# write.csv(batsdf5, file = file.path(output_today, "DensityBats_ForestPhoto.csv"))
# 01.02.2024
```


## Combine Night aggregated bat data with weather data 
### For Katrine - SRE bats with soil moisture data 
```{r}

## Now get the data that Katrine needs for the insect paper
sre.ob <- batsdf2 %>% filter(PlotType == "Open" & guild == "SRE") %>% droplevels()
sre.ob$year <- year(sre.ob$night)
sre.ob$jnight <- yday(sre.ob$night)
# 16218 obs of 12 vars 
#write.csv(sre.ob, file = file.path(output_today, "SRE_OpenBats.csv"))
# 01.02.2024

## Visually check the SRE OB dataset before sending 
# ggplot(sre.ob) + 
#   geom_count(aes(x = jnight, y = behavior, color = behavior, size = batpass)) +   facet_wrap(Site~year)
# 
# ggplot(sre.ob %>% filter(batpass >0)) + 
#   geom_count(aes(x = jnight, y = behavior, color = behavior, size = batpass)) +   facet_wrap(Site~year)
# 
# summary(sre.ob)

sre.ob <- sre.ob %>% 
  mutate(
    Site = factor(Site),
    SitePlot = factor(SitePlot), 
    SitePlotYear = factor(SitePlotYear), 
    PlotType = factor(PlotType), 
    manual.id = factor(manual.id), 
    behavior = factor(behavior), 
    guild = factor(guild),
    year = factor(year), 
    site.year = factor(paste0(Site, "-", year))) 


### Combine with bat data - Tomst data 
sre.ob.weather.log <- left_join(weather.log, sre.ob)
dim(sre.ob.weather.log)
# 12302    20
summary(sre.ob.weather.log) # 140 NAs 
# Remove observations where we had weather data but no sre bat data 
sre.ob.weather.log1 <- sre.ob.weather.log %>% filter(complete.cases(SitePlotYear)) 
dim(sre.ob.weather.log1)
# 12162    20 
# lost 140 weather nights 

# Add in hemisphere photo data 
sre.ob.weather.log2 <- left_join(sre.ob.weather.log1, hemi) 
dim(sre.ob.weather.log2)
# 12162    21
summary(sre.ob.weather.log2)
sum(sre.ob.weather.log2$batpass)
# 29948
#write.csv(sre.ob.weather.log2 , file = file.path(output_today, "sre.open_se.weather_log.weather.csv")) 
# Folder: NightAggBats_2024-02-01"
# 01.02.2024

### Combine with bat data - se.norge data only (no loggers)
sre.weather <- left_join(sre.ob, weather.se)
sre.weather1 <- left_join(sre.weather, hemi) 
dim(sre.weather1)
# 16218    17    
summary(sre.weather1)
sum(sre.weather1$batpass)
# 39260 
#write.csv(sre.weather1 , file = file.path(output_today, "sre.open_se.weather.csv")) 
# Folder: NightAggBats_2024-02-01"
# 01.02.2024

```

