---
title: "GeneralFiguresSummaries"
output: html_document
date: "2024-02-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(data.table)
library(tidyverse)
library(beepr)
library(lubridate)
library(purrr)
library(janitor)
#renv::install("rstudio/renv")
library(renv)
library(stringr)
library(beepr)
library(kableExtra)
library(papeR)
library(skimr)
library(vtable)
library(ggdark)
library(RColorBrewer)
library(cowplot)
library(readxl)
library(readr)
library(ggstats)
library(ggpmisc)
library(gginnards)
library(ggplot2)
library(colorBlindness)
library(vegan) 
library(TMB)
library(glmmTMB)
library(DHARMa)

## Setup output directory 
output <- "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/ForDryad/4.FiguresTables/Outputs/"

file.name <- "GeneralFiguresSummaries"

todays_date <- Sys.Date()
 
dir.name <- str_c(output,"/", file.name, "_", todays_date)
dir.name
 
output_today <- dir.name
output_today

dir.create(output_today)
output_today
```


```{r}

###########################################################
## Night aggregated 
###########################################################
bats <- read_csv("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/Inputs/FF_2021_2022_NightAggregated_AllSREmid_subsetnonSREmid_3behaviors_photo_forest.csv", 
     col_types = cols(...1 = col_skip()))

bats <- bats %>% mutate(jnight = yday(night), 
                        SitePlotYear = factor(SitePlotYear),
                        Site = factor(Site), 
                        SitePlot = factor(SitePlot), 
                        PlotType = factor(PlotType), 
                          manual.id = factor(manual.id), 
                          behavior = factor(behavior), 
                          guild = factor(guild), 
                          VegType = factor(VegType),
                          VegCover = factor(VegCover), 
                          PlotSize.m2 = as.numeric(PlotSize.m2),
                          year = year(night),
                          SiteYear = factor(paste0(Site, "-", year))) 

summary(bats$day_length)
  # Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  # 12.48   16.06   17.56   17.05   18.45   18.78

sd(bats$day_length)
# 1.65803

sum(bats$batpass)
# 106519
###########################################################
## Add Se.Norge weather 
###########################################################

weather <- read_csv("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/Inputs/se.norge_precip_temp_combined_2021_2022.csv", 
     col_types = cols(...1 = col_skip()))

weather <- weather %>% mutate(year = year(night), 
                              SiteYear = factor(paste0(Site, "-", year))) 

bats1 <- left_join(bats, weather)

summary(bats1)
dim(bats1)
# 244,470     31
```

## Prepare factor level order and color pallettes for plotting 
```{r}
bats1 <- bats %>% 
  dplyr::mutate(season = factor(case_when(
    jnight %in% 124:170 ~ "Early", 
    jnight %in% 171:217 ~ "Medium", 
    jnight %in% 218:263 ~ "Late"))) %>% 
  dplyr::mutate(season = 
                  factor(season, levels=c("Early", "Medium", "Late"))) 
summary(bats1)

summary(bats1$season)

### Manual ID taxa
levels(bats1$manual.id)
# "EPNI" "LR1"  "LR2"  "MR1"  "MYOT" "NYNO" "NoID" "PAUR" "PINA" "PIPY"

bats1$manual.id <- factor(bats1$manual.id, levels=c("MYOT", "PAUR", 
                             "PIPY", "PINA", "MR1",
                             "EPNI", "LR1",  "LR2", "NYNO",
                             "NoID")) 
levels(bats1$manual.id)

bats1 <- bats1 %>% 
  mutate(taxa = factor(case_when(
    manual.id == "MYOT" ~ "Myotis spp.", 
    manual.id == "PAUR" ~ "P. auritus", 
    manual.id == "PIPY" ~ "P. pygmaeus", 
    manual.id == "PINA" ~ "P. nathusii", 
    manual.id == "MR1" ~ "Pipistrellus spp.",
    manual.id == "EPNI" ~ "E. nilssonii", 
    manual.id == "LR1" ~ "LR1",
    manual.id == "LR2" ~ "LR2", 
    manual.id == "NYNO" ~ "N. noctula",
    manual.id == "NoID"  ~ "NoID")))


bats1$taxa <- factor(bats1$taxa, levels=c("Myotis spp.", "P. auritus", 
                             "P. pygmaeus", "P. nathusii", "Pipistrellus spp.",
                             "E. nilssonii", "LR1",  "LR2", "N. noctula",
                             "NoID")) 




mid.cols <- c( "#c5dcf1","#5f768b",
              "#fff68f","#ccc472", "#999355",
              "#FFB6C1", "#b27f87", "#7f5b60", "#4c3639",
              "gray") 
cvdPlot(replacePlotColor(displayColors(mid.cols)))


### Guild 
levels(bats1$guild)
bats1$guild <- factor(bats1$guild, levels=c("SRE", "MRE", "LRE", "NoID")) 
guild.cols <- c("#c5dcf1", "#fff68f", "#FFB6C1", "gray")
cvdPlot(replacePlotColor(displayColors(guild.cols)))


### Plot Type 
levels(bats1$PlotType)
#"Canopy"   "Interior" "Open"  
bats1$PlotType <- factor(bats1$PlotType, levels=c("Open", "Interior", "Canopy"))
levels(bats1$PlotType)
plot.cols <- c("#F57969", "#669F85", "#6D5AA1") 


## Behavior 
levels(bats1$behavior)
#            "Commuting"  "Feeding"   "Social"
behav.cols <- c("black", "darkgray", "lightgray") 



### Subsets that will be useful for plotting 

# reassign batpass values over 30 to 30
bats1$batpass30 <- bats1$batpass
bats1$batpass30[bats1$batpass>30] <- 30
## Do NOT use this for modelling 

# reassign batpass values over 10 to 10
bats1$batpass10 <- bats1$batpass
bats1$batpass10[bats1$batpass>10] <- 10
## Do NOT use this for modelling 

## All SRE commuting 
sre.c <- bats1 %>% 
         filter(batpass > 0) %>% 
         filter(guild == "SRE") %>% 
         filter(behavior == "Commuting") %>% 
         droplevels()

# reassign batpass values over 30 to 30
sre.c$batpass30 <- sre.c$batpass
sre.c$batpass30[sre.c$batpass>30] <- 30
## Do NOT use this for modelling 

### Myotis commuting 
myot.c <- bats1 %>%
         filter(manual.id == "MYOT") %>% 
         filter(batpass > 0) %>% 
         filter(guild == "SRE") %>% 
         filter(behavior == "Commuting") %>% 
         droplevels()

# reassign batpass values over 30 to 30
myot.c$batpass30 <- myot.c$batpass
myot.c$batpass30[myot.c$batpass>30] <- 30
## Do NOT use this for modelling 

### Myotis feeding 
myot.f <- bats1 %>%
         filter(manual.id == "MYOT") %>% 
         filter(batpass > 0) %>% 
         filter(guild == "SRE") %>% 
         filter(behavior == "Feeding") %>% 
         droplevels()

# reassign batpass values over 30 to 30
myot.f$batpass30 <- myot.f$batpass
myot.f$batpass30[myot.f$batpass>30] <- 30
## Do NOT use this for modelling 
  

```


## Summaries of bat acoustic analysis 

 19001 files analyzed for Mathilde's thesis
 84873 files analyzed from the rest of the 2021 and 2022 subset 
 Total = 103874 files through manual acoustic analysis for this manuscript. 
 
 484303 (total files) - 222521 (bat passes)
 261782 noise files removed in *2021*
 
 494268 (total files) - 194415 (bat passes)
 299853 noise files removed in *2022*

 484303 (total files) + 494268 (bat passes)
 978571 recording total for 2021 and 2022 combined (noise included)

 194415 + 222521 
 416936 # bat passes detected 2021 and 2022 combined
 
## Standard results

```{r}
## The number of unique detector nights for each year and combined
bats1$jnight.f <- factor(bats1$jnight)
bnights <- bats1 %>% select(c(SitePlotYear, year, night)) %>% distinct() 
table(bnights$year)
# 2021 2022 
# 3802 4347 

table(bats1$guild)
#   SRE   MRE   LRE  NoID 
# 48894 73341 97788 24447

b1 <- bats1 %>% dplyr::group_by(guild) %>% dplyr::summarize(batpass = sum(batpass)) 
b1
#   guild batpass
#   <fct>   <dbl>
# 1 SRE     77377
# 2 MRE     12466
# 3 LRE     15812
# 4 NoID      864


b2 <- bats1 %>% dplyr::group_by(manual.id) %>% dplyr::summarize(batpass = sum(batpass)) 
b2

sum(b2$batpass)


b3 <- bats1 %>% dplyr::group_by(behavior) %>% dplyr::summarize(batpass = sum(batpass)) 
b3
# 1 Commuting   83145
# 2 Feeding     15490
# 3 Social       7884

#83145 + 15490 + 7884

83145/106519
# 0.780565

15490/106519
# 0.1454201

7884/106519
# 0.07401496

## Now fore SRE only

b4 <- bats1 %>% filter(manual.id == "MYOT") %>% droplevels() %>%  dplyr::group_by(behavior) %>% dplyr::summarize(batpass = sum(batpass)) 
b4
# 1 Commuting   61006
# 2 Feeding     13775
# 3 Social        198

sum(b4$batpass)
# 74979


61006/74979
# 0.8136412

13775/74979
# 0.1837181

198/74979
#  0.002640739


## When were the brown long-eared bats recorded?

ggplot(bats1 %>% filter(manual.id == "PAUR", batpass >0) %>% droplevels(), aes(x = jnight, y = batpass)) + geom_point(color = "orange", size = 3, alpha = 0.5) + theme_minimal() + facet_wrap(season~PlotType)

ptest <- bats1 %>% filter(manual.id == "PAUR", batpass >0 ) 

ptest1 <- ptest %>% group_by(PlotType, season) %>% dplyr::summarise(batpass = sum(batpass)) 
ptest1

#   PlotType season batpass
#   <fct>    <fct>    <dbl>
# 1 Open     Early      194
# 2 Open     Medium     448
# 3 Open     Late       903

# 4 Interior Early       56
# 5 Interior Medium     144
# 6 Interior Late       168

# 7 Canopy   Early       51
# 8 Canopy   Medium     150
# 9 Canopy   Late       284

## Do the same for Myotis 

mtest <- bats1 %>% filter(manual.id == "MYOT", batpass >0 ) 

mtest1 <- mtest %>% group_by(PlotType, season) %>% dplyr::summarise(batpass = sum(batpass)) 
mtest1

# 1 Open     Early     9190
# 2 Open     Medium   13578
# 3 Open     Late     14947
# 
# 4 Interior Early     4647
# 5 Interior Medium    5393
# 6 Interior Late      6366
# 
# 7 Canopy   Early     3328
# 8 Canopy   Medium    9465
# 9 Canopy   Late      8065

## Number of SRE bats recorded overall
s <- bats1 %>% filter(guild == "SRE") %>% droplevels()

## Number of total bat passes detected with each plot type

plots <- bats1 %>% group_by(PlotType) %>% dplyr::summarize(batpass = sum(batpass)) 

plots
#   PlotType batpass
#   <fct>      <dbl>
# 1 Open       49911
# 2 Interior   24991
# 3 Canopy     31617 

# 106519 bat passes total 
49911/106519 *100
# 46.85643 in open habitats 
24991 /106519 *100
# 23.46154 in open habitats 
31617/106519 *100
# 29.68203 in open habitats 

### Bat activity in response to temperature and rain 

# Detector nights when at least 10 bat passes were detected (per manual.id)
ggplot(bats1 %>% filter(batpass>10), aes(x = temperature, y = rainfall)) + geom_point(color = "#DAB82A", size = 2, alpha = 0.8) + theme_minimal()

# Detector nights when zero bat passes were detected (per manual.id)
ggplot(bats1 %>% filter(batpass == 0), aes(x = temperature, y = rainfall)) + geom_point(color = "#DAB82A", size = 2, alpha = 0.8) + theme_minimal()

#####
temp <- ggplot(bats1 %>% filter(batpass > 0), aes(x = temperature, y = batpass)) + geom_point(color = "#DAB82A", size = 2, alpha = 0.8) + theme_minimal()

rain <- ggplot(bats1 %>% filter(batpass > 0), aes(x = rainfall, y = batpass)) + geom_point(color = "#DAB82A", size = 2, alpha = 0.8) + theme_minimal()

cowplot::plot_grid(temp, rain)

#####
temp <- ggplot(bats1 %>% filter(batpass > 0), aes(x = temperature, y = batpass)) + geom_point(color = "#DAB82A", size = 2, alpha = 0.8) + theme_minimal() + xlim(c(0, 7.5)) + ylim(0, 50)

rain <- ggplot(bats1 %>% filter(batpass > 0), aes(x = rainfall, y = batpass)) + geom_point(color = "#DAB82A", size = 2, alpha = 0.8) + theme_minimal() + xlim(c(20, 55)) + ylim(0, 200)

cowplot::plot_grid(temp, rain)

temptest <- bats1 %>% filter(batpass>0, temperature > 9)
sum(temptest$batpass)
105558/106519 *100
# 99.09781 %

raintest <- bats1 %>% filter(batpass>0, rainfall < 20)
sum(raintest$batpass)
105742/106519 *100
# 99.27055 %

wtest <- bats1 %>% filter(batpass>0, rainfall < 20, temperature > 9)
sum(wtest$batpass)
104781/106519 *100
# 98.36837

```


# Supplementary materials describng survey effort 
*Supplementary materials, Figure S1* 
```{r}

bats1$active.night <- "TRUE"
b21 <- bats1 %>% filter(year == 2021) %>% droplevels()
b22 <- bats1 %>% filter(year == 2022) %>% droplevels()

## 2021 

S1.21.l <- ggplot(b21) + 
  geom_point(data = b21[b21$batpass>0,], 
             aes(x = night, y = Site, color = PlotType), 
             shape = 19,  alpha = 0.5) +  
  facet_wrap(~PlotType, nrow=3) + 
  scale_color_manual(values = plot.cols) + 
  xlab("2021") + ylab(" ") +
  ggtitle("Bat activity") + 
  theme(legend.position="none") +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        text = element_text(size = 25),
        axis.line = element_line(colour = "black"))
#S1.21.l

S1.21.r <- ggplot(b21) + 
  geom_point(aes(x = night, y = Site, color = active.night), 
             shape = 19,  alpha = 0.5) +  
  facet_wrap(~PlotType, nrow=3) + 
  scale_color_manual(values = "#DAB82A") + 
  xlab("2021") + ylab(" ") +
  ggtitle("Active detector nights") + 
  theme(legend.position="none") +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        text = element_text(size = 25),
        axis.line = element_line(colour = "black"))
#S1.21.r

#windows()
S1.21 <- cowplot::plot_grid(S1.21.l, S1.21.r)

#S1.21

## 2022

S1.22.l <- ggplot(b22) + 
  geom_point(data = b22[b22$batpass>0,], 
             aes(x = night, y = Site, color = PlotType), 
             shape = 19,  alpha = 0.5) +  
  facet_wrap(~PlotType, nrow=3) + 
  scale_color_manual(values = plot.cols) + 
  xlab("2022") + ylab(" ") +
  ggtitle("Bat activity") + 
  theme(legend.position="none") +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        text = element_text(size = 25),
        axis.line = element_line(colour = "black"))
#S1.22.l


S1.22.r <- ggplot(b22) + 
  geom_point(aes(x = night, y = Site, color = active.night), 
             shape = 19,  alpha = 0.5) +  
  facet_wrap(~PlotType, nrow=3) + 
  scale_color_manual(values = "#DAB82A") + 
  xlab("2022") + ylab(" ") +
  ggtitle("Active detector nights") + 
  theme(legend.position="none") +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        text = element_text(size = 25),
        axis.line = element_line(colour = "black"))
#S1.22.r

S1.22 <- cowplot::plot_grid(S1.22.l, S1.22.r)
#windows()
#S1.22

## Now all together 
surveyeffort <- cowplot::plot_grid(S1.21, S1.22, ncol = 2, labels = c("a.", "b."))

surveyeffort

ggsave(path = output_today, filename = "SurveyEffort.tiff", width = 23, height = 14, device='tiff', dpi=300) 


# What was the average number of detector nights per SitePlotYear ?
summary(bnights)
head(bnights)

bnights1 <- bnights %>%  group_by(SitePlotYear) %>% 
  dplyr::summarise(n  = sum(n())) 

head(bnights1)
summary(bnights1)
# Number of nights per detector site
 #       SitePlotYear       n        
 # FF01-CB-2021: 1    Min.   : 44.0  
 # FF01-CB-2022: 1    1st Qu.:109.0  
 # FF01-IB-2021: 1    Median :116.0  
 # FF01-IB-2022: 1    Mean   :118.1  
 # FF01-OB-2021: 1    3rd Qu.:137.0  
 # FF01-OB-2022: 1    Max.   :140.0  
 # (Other)     :63 
sd(bnights1$n)
# 19.39765

bnights21 <- bnights %>% filter(year == "2021") %>% 
  droplevels() %>%  group_by(SitePlotYear) %>% 
  dplyr::summarise(n  = sum(n()))
summary(bnights21)
 #       SitePlotYear       n        
 # FF01-CB-2021: 1    Min.   : 44.0  
 # FF01-IB-2021: 1    1st Qu.:107.0  
 # FF01-OB-2021: 1    Median :110.0  
 # FF02-CB-2021: 1    Mean   :105.6  
 # FF02-IB-2021: 1    3rd Qu.:112.8  
 # FF02-OB-2021: 1    Max.   :123.0  
 # (Other)     :30            

bnights22 <- bnights %>% filter(year == "2022") %>% 
  droplevels() %>%  group_by(SitePlotYear) %>% 
  dplyr::summarise(n  = sum(n())) 
summary(bnights22)
#        SitePlotYear       n        
#  FF01-CB-2022: 1    Min.   : 96.0  
#  FF01-IB-2022: 1    1st Qu.:131.0  
#  FF01-OB-2022: 1    Median :137.0  
#  FF02-CB-2022: 1    Mean   :131.7  
#  FF02-IB-2022: 1    3rd Qu.:137.0  
#  FF02-OB-2022: 1    Max.   :140.0  
#  (Other)     :27 

```

### Compare between manual and automatic acoustic analysis 
*Supplementary Figure S2.*

More info on background for these figures: 
https://indrajeetpatil.github.io/ggstatsplot/reference/ggbarstats.html
```{r}
###########################################################
## Unaggregated bat acoustic data
###########################################################

rawbat <- read_csv("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/Inputs/ManualAnalaysis21_22_combined_datetime_PlotType_Guild.csv", 
     col_types = cols(...1 = col_skip()))
# 108989 

rawbat <- rawbat %>% mutate(AUTO.ID = factor(AUTO.ID),
                            manual.id = factor(manual.id),
                            behavior = factor(behavior),
                            guild = factor(guild),
                            year = factor(year),
                            Site = factor(Site), 
                        SitePlot = factor(SitePlot), 
                        PlotType = factor(PlotType)) 

levels(rawbat$manual.id)
table(rawbat$manual.id)
levels(rawbat$AUTO.ID)


rbats.0 <- rbats  %>% filter(manual.id != "Noise") %>% droplevels() %>% 
  mutate(taxa = factor(case_when(
    manual.id == "MYOT" ~ "Myotis spp.", 
    manual.id == "PAUR" ~ "P. auritus", 
    manual.id == "PIPY" ~ "P. pygmaeus", 
    manual.id == "PINA" ~ "P. nathusii", 
    manual.id == "MR1" ~ "Pipistrellus spp.",
    manual.id == "EPNI" ~ "E. nilssonii", 
    manual.id == "LR1" ~ "LR1",
    manual.id == "LR2" ~ "LR2", 
    manual.id == "NYNO" ~ "N. noctula",
    manual.id == "NoID"  ~ "NoID")))


rbats.0 $taxa <- factor(rbats.0 $taxa, levels=c("Myotis spp.", "P. auritus", 
                             "P. pygmaeus", "P. nathusii", "Pipistrellus spp.",
                             "E. nilssonii", "LR1",  "LR2", "N. noctula",
                             "NoID")) 

# 5116 NAs for AUTO.ID and INDIR for recordings that had multiple bats/were parsed. Fix this here:

### Subset for the NA observations 
nas <- rawbat %>% filter(is.na(AUTO.ID)) # 5116
summary(nas)

# Select the auto id and indir for these files 
fix <- nas %>% select(file.name) %>% distinct() # 5029
fix1 <- left_join(fix, rawbat) %>% drop_na()
summary(fix1)
fix2 <- fix1 %>% select(file.name, INDIR, AUTO.ID) %>% distinct()

# Attach the indir and autoid for wher previously there were nas 
nas1 <- nas %>% select(-c(AUTO.ID, INDIR)) 
summary(nas1)
nas2 <- left_join(nas1, fix2)
summary(nas2)

# Remove the nas from the rawbat dataset and then replace with actual values
rawbat1 <- rawbat %>% drop_na(AUTO.ID)
dim(rawbat)
#108989     22

dim(rawbat1)
#103873     22
#108989 - 103873 = 5116, good 

dim(nas2)
#5116   22
# good

rawbat2 <- merge(rawbat1, nas2, all = TRUE)
dim(rawbat2)
#108989     22, good

summary(rawbat2) 

rawbat3 <- rawbat2 %>% mutate(auto = factor(case_when(
  AUTO.ID == "BARBAR" ~ "BABA",
  AUTO.ID == "EPTNIL" ~ "EPNI",
  AUTO.ID == "EPTSER" ~ "EPSE",
  AUTO.ID %in% c("MYOALC", "MYOBEC", "MYOBRA",
                 "MYODAS", "MYODAU", "MYOMYO", 
                 "MYOMYS", "MYONAT") ~ "MYOT",
  AUTO.ID == "NYCNOC" ~ "NYNO",
  AUTO.ID == "NYCLEI" ~ "NYLE",
  AUTO.ID == "PIPNAT" ~ "PINA", 
  AUTO.ID == "PIPPIP" ~ "PIPI", 
  AUTO.ID == "PIPPYG" ~ "PIPY", 
  AUTO.ID == "PLEAUR" ~ "PAUR",
  AUTO.ID == "PLEAUS" ~ "PAUS", 
  AUTO.ID == "VESMUR" ~ "VEMU", 
  AUTO.ID == "NoID" ~ "NoID"
))) %>% 
  mutate(auto.guild = factor(case_when(
  AUTO.ID == "BARBAR" ~ "SRE",
  AUTO.ID == "EPTNIL" ~ "LRE",
  AUTO.ID == "EPTSER" ~ "LRE",
  AUTO.ID %in% c("MYOALC", "MYOBEC", "MYOBRA",
                 "MYODAS", "MYODAU", "MYOMYO", 
                 "MYOMYS", "MYONAT") ~ "SRE",
  AUTO.ID == "NYCNOC" ~ "LRE",
  AUTO.ID == "NYCLEI" ~ "LRE",
  AUTO.ID == "PIPNAT" ~ "MRE", 
  AUTO.ID == "PIPPIP" ~ "MRE", 
  AUTO.ID == "PIPPYG" ~ "MRE", 
  AUTO.ID == "PLEAUR" ~ "SRE",
  AUTO.ID == "PLEAUS" ~ "SRE", 
  AUTO.ID == "VESMUR" ~ "LRE", 
  AUTO.ID == "NoID" ~ "NoID"  
  ))) 

summary(rawbat3)


rbats <- rawbat3


summary(rbats$auto)
summary(rbats$manual.id)

levels(rbats$manual.id)
# "EPNI"  "LR1"   "LR2"   "MR1"   "MYOT"  "NYNO"  "NoID" 
# "Noise" "PAUR"  "PINA"  "PIPY" 

table(rbats$manual.id)

rbats$manual.id <- factor(rbats$manual.id, 
                          levels = c(
  "MYOT", "PAUR", 
  "PIPY", "PINA",  "MR1",
  "EPNI", "LR1", "LR2", "NYNO",
  "NoID", "Noise"))
levels(rbats$manual.id)
table(rbats$manual.id)

levels(rbats$auto)
# [1] "BABA" "EPNI" "EPSE" "MYOT" "NYLE" "NYNO" "NoID" "PAUR"
#  [9] "PAUS" "PINA" "PIPI" "PIPY" "VEMU"



levels(rbats$AUTO.ID)
# "BARBAR" "EPTNIL" "EPTSER" "MYOALC" "MYOBEC" "MYOBRA" "MYODAS" "MYODAU" "MYOMYO"
# "MYOMYS" "MYONAT" "NYCLEI" "NYCNOC" "NoID"   "PIPNAT" "PIPPIP" "PIPPYG" "PLEAUR"
# "PLEAUS" "VESMUR"

rbats$AUTO.ID <- factor(rbats$AUTO.ID, levels = c(
  "MYOALC", "MYOBEC", "MYOBRA", "MYODAS", "MYODAU", 
  "MYOMYO", "MYOMYS", "MYONAT",
  "PLEAUR", "PLEAUS", "BARBAR",
  "PIPNAT", "PIPPIP", "PIPPYG",
  "EPTNIL", "EPTSER", "VESMUR", "NYCLEI", "NYCNOC",
  "NoID")) 

levels(rbats$auto)

auto.cols <- c( "#c5dcf1","#5f768b", "#788ea2", "#34546e",
              "#fff68f","#ccc472", "#999355",
              "#FFB6C1", "#ffe1e6", "#7f5b60", "#4c3639",
              "gray") 

cvdPlot(replacePlotColor(displayColors(auto.cols)))


### rbats Guild and Auto Guild
levels(rbats$guild)
rbats$guild <- factor(rbats$guild, levels=c("SRE", "MRE", "LRE", "NoID", "Noise")) 
guild.cols <- c("#c5dcf1", "#fff68f", "#FFB6C1", "gray", "black")
cvdPlot(replacePlotColor(displayColors(guild.cols)))

levels(rbats$auto.guild)
rbats$auto.guild <- factor(rbats$auto.guild, levels=c("NoID", "LRE", "MRE", "SRE")) 
auto.guild.cols <- c("gray", "#FFB6C1", "#fff68f", "#c5dcf1")
cvdPlot(replacePlotColor(displayColors(auto.guild.cols)))

  # "MYOT", "PAUR", "PAUS", "BABA",
  # "PIPY", "PINA",  "PIPI",
  # "EPNI", "EPSE", "VEMU", "NYLE", "NYNO",
  # "NoID"
rbats$auto <- factor(rbats$auto, levels = c(
  "NoID",
  "NYNO", "NYLE", "VEMU", "EPSE", "EPNI", 
  "PIPI", "PINA",  "PIPY",
  "BABA", "PAUS",  "PAUR", "MYOT"
  ))
levels(rbats$auto)

id_bar <- 
  ggstatsplot::ggbarstats(rbats, x = auto, y=manual.id, 
  type = "nonparametric", paired = TRUE,
  sample.size.label.args = list(size = 3)) +
  scale_fill_manual(values = c(
  "MYOT" = "#c5dcf1",
  "PAUR" = "#5f768b", 
  "PAUS" = "#788ea2", 
  "BABA" = "#34546e",
  "PIPY" = "#fff68f", 
  "PIPI" = "#ccc472", 
  "PINA" = "#999355",
  "EPNI" = "#FFB6C1",
  "EPSE" = "#ffe1e6",
  "VEMU" = "#7f5b60",
  "NYLE" = "#9f8e90",
  "NYNO" = "#4c3639",
  "NoID" = "gray"
  )) +
  xlab("Manually Identified Bat Taxa") +
  guides(fill=guide_legend("Auto ID")) +
  theme(text = element_text(size = 15), 
        legend.position="left",
        axis.title.x = element_text(size = 15),
        plot.subtitle = element_text(size = 15),
        legend.text = element_text(size = 13)) +
  ggtitle("", subtitle = "n = 108,989 bat passes") + 
  theme(plot.title = element_text(size = 13, face = "italic"))

id_bar1 <- delete_layers(id_bar, "GeomLabel") # remove percent lables
id_bar1
#windows()


id_bar_table <- id_bar$data # write table of results 
#write.csv(id_bar_table, file = file.path(output_today("id_bar_table.perc.csv"))) 

          # NOTES on ggbar stats: 
#"Decides whether proportion test for x variable is to be carried out for each level of y. #Defaults to results.subtitle. In ggbarstats, only p-values from this test will be #displayed."

# Only one-sided proportion test is conducted here, no McNemar's test. This is because auto and manual id levels do not perfectly match.  

# Remove noise observations from manual ID and then test 
rbats1 <- rbats %>% filter(manual.id != "Noise") %>% droplevels()

dim(rbats)
# 108989     
dim(rbats1)
# 106525     
# 108989 - 106525
# 2464 noise passes removed 

levels(rbats1$auto.guild)
# "SRE"  "MRE"  "LRE"  "NoID"

  
  
auto.guild.cols <- c("#c5dcf1", "#fff68f", "#FFB6C1", "gray")

guild_bar <- ggstatsplot::ggbarstats(
  rbats1, x= auto.guild, y=guild, 
  type = "nonparametric", paired = TRUE,
  sample.size.label.args = list(size = 3)) + 
  ggplot2::scale_fill_manual(values = c(
      "SRE" = "#c5dcf1" , "MRE" = "#fff68f", 
      "LRE" = "#FFB6C1", "NoID" = "gray")) + 
  ggplot2::xlab("Manually Identified Foraging Guilds") + 
  guides(fill=guide_legend("Auto ID")) + 
  theme(text = element_text(size = 14), 
        legend.position="right",
        axis.title.x = element_text(size = 15),
        legend.title = element_text(size = 13),
        legend.text = element_text(size = 13)) +
  ggtitle("")
guild_bar

# Double check the mcnemar test results in the figure 
g <- mcnemar.test(table(rbats1$auto.guild, rbats1$guild), correct = FALSE) 
g 
# data:  table(rbats1$auto.guild, rbats1$guild)
# McNemar's chi-squared = 15501, df = 6, p-value < 2.2e-16

manualvsauto <- cowplot::plot_grid(id_bar1, guild_bar, nrow = 1, labels = c("a.", "b."))

manualvsauto

ggsave(path = output_today, filename = "manualcsauto.tiff", width = 17, height = 8, device='tiff', dpi=300) 

# p values - Goodness of fit chi-squared test

## Now for a table 
  
### Table i. Supplementary materials 
rbats.simpl <- rbats %>% distinct(file.name, .keep_all = TRUE) 
autotab <- table(rbats.simpl$AUTO.ID) 
kable(autotab) %>%  kable_minimal()

rbats$manual.id <- factor(rbats$manual.id, levels = c(
  "MYOT", "PAUR", 
  "PIPY", "PINA", "MR1", 
  "EPNI", "LR1", "LR2", "NYNO",
  "NoID", "Noise")) 

manualtab <- table(rbats$manual.id) 
kable(manualtab) %>%  kable_minimal()

## Now for feeding only 
feeding <- rbats %>% filter(behavior == "Feeding") %>% droplevels()
feeding.mtab <- table(feeding$manual.id) 
kable(feeding.mtab) %>%  kable_minimal()

## Now for social only 
social <- rbats %>% filter(behavior == "Social") %>% droplevels()
social.mtab <- table(social$manual.id) 
kable(social.mtab) %>%  kable_minimal()

## Look at differences in SRE bat identification 

raw.sre <- rbats %>% filter(PlotType == "Open", 
                            AUTO.ID %in% 
                              c("MYOALC", "MYOBEC", "MYOBRA", "MYODAS",
                                "MYODAU", "MYOMYO", "MYOMYS", "MYONAT",
                                "BARBAR", "PLEAUR", "PLEAUS")) %>% 
  droplevels()

dim(raw.sre)
# 42419    24

table(raw.sre$manual.id)
#  MYOT  PAUR  PIPY   MR1  EPNI   LR1   LR2  NYNO  NoID Noise 
# 69635  2357  5836     5  6007    39     8     5   630   144 
```





## Fig S3
Bar charts showing the proportion of different species detected (acoustics) across sites, faceted by plot type and year. (RQ1)

```{r}

rbats.0 <- rbats  %>% filter(manual.id != "Noise") %>% droplevels() %>% 
  mutate(taxa = factor(case_when(
    manual.id == "MYOT" ~ "Myotis", 
    manual.id == "PAUR" ~ "P. auritus", 
    manual.id == "PIPY" ~ "P. pygmaeus", 
    manual.id == "PINA" ~ "P. nathusii", 
    manual.id == "MR1" ~ "Pipistrellus spp.",
    manual.id == "EPNI" ~ "E. nilssonii", 
    manual.id == "LR1" ~ "LR1",
    manual.id == "LR2" ~ "LR2", 
    manual.id == "NYNO" ~ "N. noctula",
    manual.id == "NoID"  ~ "NoID")))


rbats.0 $taxa <- factor(rbats.0 $taxa, levels=c("Myotis", "P. auritus", 
                             "P. pygmaeus", "P. nathusii", "Pipistrellus spp.",
                             "E. nilssonii", "LR1",  "LR2", "N. noctula",
                             "NoID")) 

rbats.0$PlotType <- factor(rbats.0$PlotType, levels=c("Open", "Interior", "Canopy"))
levels(rbats.0$PlotType)

# Now for only plot types, all sites combined, separate years 
taxaplot <- ggplot(data = rbats.0) + 
  aes(x = PlotType,  fill = taxa, by = PlotType) +
  geom_bar(position = "fill", stat = "prop") + 
  scale_fill_manual(values = mid.cols, name="",
                    labels = levels(rbats.0$taxa), 
                    expression(italic())) + 
  theme_minimal() + 
  facet_wrap(~year) +
  theme(legend.title=element_blank(),
        legend.text = element_text(face = "italic"),
        text=element_text(size=20),
        legend.position = "bottom") +
  ylab("") + xlab("")

taxaplot

# cvdPlot(taxaplot)
# passes colorblindess check

ggsave(path = output_today, filename = "taxabarplot.tiff", width = 12, height = 8, device='tiff', dpi=600) 

```

