
---
title: "Myotis_Feeding_GAM"
output: html_document
date: "2024-02-13"
---


```{r}
library(rgl)
library(vctrs)
library(plotly)
library(ggplot2)
library(dplyr)
library(gamm4)
library(mgcv)
library(itsadug)
library(plot3D)
library(readr)
library(stringr)
library(beepr)
library(kableExtra)
library(papeR)
library(skimr)
library(vtable)
library(ggdark)
library(RColorBrewer)
library(cowplot)
library(readxl)
library(readr)
library(ggstats)
library(ggpmisc)
library(gginnards)
library(colorBlindness)
library(vegan) 
library(TMB)
library(glmmTMB)
library(DHARMa)
library(textshape)
library(tidyr)
library(plotly)
library(MASS)

## Setup output directory 
output <- "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/ForDryad/5.BatInsectModels/Outputs"

file.name <- "M.Feed_GAM"

todays_date <- Sys.Date()
 
dir.name <- str_c(output,"/", file.name, "_", todays_date)
dir.name
 
output_today <- dir.name
output_today

dir.create(output_today)
output_today
# "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/ForDryad/5.BatInsectModels/Outputs/M.Commut_GAM_2024-02-13"


```


## Import the data 
```{r}
mydata <-read_csv("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/3. Follo Forest 2021-2023/Manuscripts/Analyses/ForDryad/2.AggregationCombineCovariates/NightAgg_BatsInsects_SRE_Open/Outputs/NightAggBatsInsects_2024-02-01/SREbatsInsects_se.Weatherphoto.csv",
                  col_types = cols(...1 = col_skip()))#----LOAD THE DATA
# 2441 obs 26 vars 

#---QUICK INITIAL LOOK AT THE 'mydata' DATA OBJECT
str(mydata)
#---fix date format for variable night
mydata$night <- as.Date(mydata$night, "%d.%m.%Y")
#---year as factor
mydata$year <- as.factor(mydata$year)
#---Site as factor
mydata$Site <- as.factor(mydata$Site)
#---SitePlotYear as factor
mydata$SitePlotYear <- as.factor(mydata$SitePlotYear)
#---new insect variable to account for nPhoto
mydata$InsectIndex <- mydata$nInsects / mydata$nPhotos

str(mydata)
head(mydata)
tail(mydata)
dim(mydata)
summary(mydata) 
names(mydata)
```


## Data exploration and preparing subsets
```{r}
#select only manual.id level MYOT and behavior level Feeding
filtered_df <- subset(mydata, manual.id == "MYOT" & behavior == "Feeding")
dim(filtered_df)

summary(filtered_df)

DF <- filtered_df
dim(DF)
# 401  27
summary(DF)
#There are no NAs for nInsect or batpass in this subset


#How many observations in 2021 vs 2022
# Create a frequency table for year
frequency_table <- table(DF$year)

# Print the frequency table
print(frequency_table)
#2021 2022 
#293  108 

##############LOOK AT THE INSECT DATA

# Count the number of rows where InsectIndex is 0
num_zeros <- sum(DF$InsectIndex == 0)

# Calculate the total number of rows in the dataframe
total_rows <- nrow(DF)

# Calculate the percentage of rows with value 0 for InsectIndex
percent_zeros <- (num_zeros / total_rows)*100
# Print the result
cat("Percent of rows with value 0 for InsectIndex:", percent_zeros, "/n")
#Percent of rows with value 0 for InsectIndex: 16.20948
#That is not so bad

#distribution of values
plot(1:nrow(DF), DF$InsectIndex, 
     pch = 16, col = "blue", 
     main = "Distribution of InsectIndex",
     xlab = "Data Point", ylab = "InsectIndex")

# Add a horizontal line at the mean
abline(h = mean(DF$InsectIndex), col = "red", lty = 2)

range(DF$InsectIndex)
df <- DF

#Replace 4 observations with values greater than 2 in InsectIndexCertain with 2
df$InsectIndex[df$InsectIndex > 2] <- 2 

plot(1:nrow(df), df$InsectIndex, 
     pch = 16, col = "blue", 
     main = "Distribution of InsectIndex",
     xlab = "Data Point", ylab = "InsectIndex")

# Add a horizontal line at the mean
abline(h = mean(df$InsectIndex), col = "red", lty = 2)


##############LOOK AT THE CanOpen variable too
plot(1:nrow(df), df$CanOpen, 
     pch = 16, cex = 0.3, col = "darkgreen", 
     main = "Distribution of CanOpen",
     xlab = "Data Point", ylab = "CanOpen")

# Add a horizontal line at the mean
abline(h = mean(df$CanOpen), col = "red", lty = 2)


##############LOOK AT THE batpass DATA
# Count the number of rows where batpass is 0
num_zeros <- sum(df$batpass == 0)

# Calculate the total number of rows in the dataframe
total_rows <- nrow(df)

# Calculate the percentage of rows with value 0 for batpass
percent_zeros <- (num_zeros / total_rows)*100

# Print the result
cat("Percent of rows with value 0 for batpass:", percent_zeros, "/n")
#Percent of rows with value 0 for batpass: 58.85287 
#That is a lot  - will most likely need a zero-inflated model

# distribution of values
plot(1:nrow(df), df$batpass, 
     pch = 16, col = "blue", 
     main = "Distribution of batpass",
     xlab = "Data Point", ylab = "batpass")

# Add a horizontal line at the mean
abline(h = mean(df$batpass), col = "red", lty = 2)
abline(h = 20, col = "red", lty = 1)
abline(h = 30, col = "green", lty = 1)


#Will have to keep an eye one the outliers, but first check if some SitePlotYear
#have very few observations


#How many observations per SitePlotYear
# Create a frequency table for year
frequency_table <- table(df$SitePlotYear)

# Print the frequency table
print(frequency_table)

# Levels to exclude: < 10 observation nights per SitePlotYear
excluded_levels <- c('FF03-OB-2021', 'FF03-OB-2022', 'FF05-OB-2022', 'FF06-OB-2022', 'FF08-OB-2022', 'FF11-OB-2021')

# Creating a subset excluding specified levels
df_subset <- df[!(df$SitePlotYear %in% excluded_levels), ]

# Dropping excluded levels completely
df_subset$SitePlotYear <- droplevels(df_subset$SitePlotYear, exclude = excluded_levels)

# Create a frequency table for year
frequency_table <- table(df_subset$SitePlotYear)

# Print the frequency table
print(frequency_table)

dim(df) #401 rows
dim(df_subset) #364 rows

plot(1:nrow(df_subset), df_subset$batpass, 
     pch = 16, col = "blue", 
     main = "subset SitePlotYear with min 10 observ nights",
     xlab = "Data Point", ylab = "batpass")

# Add a horizontal line at the mean
abline(h = mean(df_subset$batpass), col = "red", lty = 2)
abline(h = 30, col = "red", lty = 1)


#distribution of CanOpen variable for the subsetted data

plot(1:nrow(df_subset), df_subset$CanOpen, 
     pch = 16, cex = 0.3, col = "darkgreen", 
     main = "Distribution of CanOpen",
     xlab = "Data Point", ylab = "CanOpen")

# Add a horizontal line at the mean
abline(h = mean(df_subset$CanOpen), col = "red", lty = 2)



#Not use this - but just for visual exploration
df_subset20 <- df_subset

#Replace x observations with values greater than 20 for batpass with 20
df_subset20$batpass[df_subset20$batpass > 20] <- 20 

#look at subsetted batpass data with max value 20
par(mfrow = c(1, 1))
plot(1:nrow(df_subset20), df_subset20$batpass, 
     pch = 16, col = "blue", 
     main = "subset SitePlotYear with min 10 observ nights, max value 20",
     xlab = "Data Point", ylab = "batpass")

# Add a horizontal line at the mean
abline(h = mean(df_subset20$batpass), col = "red", lty = 2)
```


## Compare site-years for insect abundance and feeding activity 
"#F57969"
```{r}
summary(DF)
summary(df)

## arrange sites according to increasing PC1 
df1 <- df %>% 
  dplyr::mutate(SiteYear = factor(paste0(Site, "-", year))) %>%
           dplyr::select(c(SitePlotYear, SiteYear, year, Site, CanOpen)) %>%
  arrange(year, CanOpen) 

sites <- df1 %>% select(SiteYear) %>% distinct()
neworder <- sites$SiteYear
df$SiteYear1 <- factor(df$SiteYear, levels = neworder)

# Plot the
ii <- ggplot(df, aes(x = SiteYear1, y = InsectIndex)) + 
  geom_boxplot(aes(fill = CanOpen)) + 
  scale_fill_gradient(low = "#f68678", high = "black") + 
  scale_x_discrete(labels=c("FF07-2021" = "07", "FF07-2022" = "07-22", 
                            "FF04-2021" = "04-21", "FF04-2022" = "04-22", 
                            "FF05-2021" = "05-21", "FF05-2022" = "05-22", 
                            "FF02-2021" = "02-21", "FF02-2022" = "02-22", 
                            "FF08-2021" = "08-21", "FF08-2022" = "08-22", 
                            "FF11-2021" = "11-21", "FF11-2022" = "11-22", 
                            "FF01-2021" = "01-21", "FF01-2022" = "01-22", 
                            "FF03-2021" = "03-21", "FF03-2022" = "03-22", 
                            "FF12-2021" = "12-21", "FF12-2022" = "12-22", 
                            "FF06-2021" = "06-21", "FF06-2022" = "06-22", 
                            "FF09-2021" = "09-21", "FF09-2022" = "09-22", 
                            "FF10-2021" = "10-21", "FF10-2022" = "10-22")) + 
  theme_minimal() + 
  theme(legend.position = "bottom") +
  guides(fill=guide_legend(title="Canopy openness")) + 
  xlab("") + ylab("Insect index") 
ii 

bb <- ggplot(df, aes(x = SiteYear1, y = batpass)) + 
  geom_boxplot(aes(fill = CanOpen)) + 
  scale_fill_gradient(low = "#f68678", high = "black") +
  scale_x_discrete(labels=c("FF07-2021" = "07", "FF07-2022" = "07-22", 
                            "FF04-2021" = "04-21", "FF04-2022" = "04-22", 
                            "FF05-2021" = "05-21", "FF05-2022" = "05-22", 
                            "FF02-2021" = "02-21", "FF02-2022" = "02-22", 
                            "FF08-2021" = "08-21", "FF08-2022" = "08-22", 
                            "FF11-2021" = "11-21", "FF11-2022" = "11-22", 
                            "FF01-2021" = "01-21", "FF01-2022" = "01-22", 
                            "FF03-2021" = "03-21", "FF03-2022" = "03-22", 
                            "FF12-2021" = "12-21", "FF12-2022" = "12-22", 
                            "FF06-2021" = "06-21", "FF06-2022" = "06-22", 
                            "FF09-2021" = "09-21", "FF09-2022" = "09-22", 
                            "FF10-2021" = "10-21", "FF10-2022" = "10-22")) + 
  theme_minimal() + 
  theme(legend.position = "none") +
  xlab("") + ylab("Myotis feeding activity") 
bb


cowplot::plot_grid(bb, ii, nrow = 2, labels = c("a.", "b."))

```



## Fit a GAM - feeding activity subset 
```{r}
#I did run GAMMs with df_subset20 (not included in this R script) but df_subset also provided a good fit to the data
#So we will use the df_subset without pruning values >20 to 20

summary(dfs)
m1nb <- gam(batpass ~ s(InsectIndex) + year + s(Site, bs = "re"), metod="REML",family= "nb()",  data = dfs)

m2nb <- gam(batpass ~ s(InsectIndex) + s(InsectIndex,CanOpen) + year + s(Site, bs = "re"), metod="REML", family= "nb()",data = dfs)

m3nb <- gam(batpass ~ s(InsectIndex,CanOpen) + year + s(Site, bs = "re"), metod="REML",family= "nb()", data = dfs)

m1zip <- gam(batpass ~ s(InsectIndex) + year + s(Site, bs = "re"), metod="REML",family= "ziP()",  data = dfs)

m2zip <- gam(batpass ~ s(InsectIndex) + s(InsectIndex,CanOpen) + year + s(Site, bs = "re"), metod="REML", family= "ziP()",data = dfs)

m3zip <- gam(batpass ~ s(InsectIndex,CanOpen) + year + s(Site, bs = "re"), metod="REML",family= "ziP()", data = dfs)

#Compare models
AIC(m1nb,m2nb, m3nb, m1zip, m2zip, m3zip)
#            df      AIC
#
#m1nb  18.98071 1179.388 
#m2nb  25.69126 1171.545 *Low
#m3nb  25.41831 1170.999 *Lowest
#m1zip 22.76598 1661.923
#m2zip 40.77491 1505.054
#m3zip 40.77487 1505.055

summary(m1nb)
summary(m2nb)
summary(m3nb)
par(mfrow = c(2, 2))
gam.check(m1nb) #k index too low
par(mfrow = c(2, 2))
gam.check(m2nb) #looks good
par(mfrow = c(2, 2))
gam.check(m3nb) #looks good


### Supplementary materials 

#######################################################################################
######### Use a 3D plot for the paper #################################################
#######################################################################################

#Prediction for all Sites and both years
new_data <- expand.grid(
  InsectIndex = seq(min(dfs$InsectIndex), max(dfs$InsectIndex), length.out = 50),
  CanOpen = unique(dfs$CanOpen),
  year = unique(dfs$year),
  Site = unique(dfs$Site))

# Make predictions
predictions <- predict(m3nb, new_data, type = "response", se.fit = TRUE)

# Extract predicted values and standard errors
pred_values <- predictions$fit
se <- predictions$se.fit

# Combine predictions with grid data
prediction_data <- cbind(new_data, pred_values, se)

# head(prediction_data)
# tail(prediction_data)
# # Create a 3D surface plot with rgl
with(prediction_data, {
  plot3d(CanOpen, InsectIndex, matrix(pred_values, ncol = length(unique(prediction_data$InsectIndex))),
         col = terrain.colors(100), type = "h", size = 0.5,
         xlab = "canopy openness", ylab = "insect abundance", zlab = "batpass",
         main = "")
  rgl.postscript("3d_plot.eps", fmt = "eps")
})



###### use plot_ly to try to get a slightly nicer visualization 

length(unique(prediction_data$CanOpen)) # 17 
length(unique(prediction_data$InsectIndex)) # 50 


#z <- matrix(predict(m3nb, newdata = new_data), 374, 50)
InsectIndex = seq(min(dfs$InsectIndex), max(dfs$InsectIndex), length.out = 15) 
CanOpen = unique(dfs$CanOpen)
#18700/50


summary(dfs$batpass)
summary(prediction_data$pred_values)
dfs$batpass1 <- dfs$batpass
dfs$batpass1[dfs$batpass1 > 42] <- 40 
# Makes it possible to plot the raw data in the same range as the predictions. 

z <- matrix(pred_values, ncol = 5)
plot_ly(x = ~CanOpen, y = ~new_data$InsectIndex, z = z, type = "surface") %>%
  layout(
    scene = list(
      xaxis = list(title = "Canopy openness"),
      yaxis = list(title = "Insect index"),
      zaxis = list(title = "Feeding passes per night"))) %>% 
  add_markers(x = ~dfs$CanOpen, y= ~dfs$InsectIndex, z=dfs$batpass1)  

ve(path = output_today, filename = "FeedingGAMPred.tiff", width = 12, height = 8, device='tiff', dpi=600) 

summary(dfs$CanOpen)
summary(new_data$CanOpen)
summary(prediction_data$CanOpen)
summary(CanOpen)

summary(dfs$InsectIndex)
summary(new_data$InsectIndex)
summary(prediction_data$InsectIndex)
summary(InsectIndex)

summary(dfs$batpass)
summary(prediction_data$pred_values)

```




## Figure 3 - Insect abundance vs canopy openness 
```{r}

# Levels to exclude: < 10 observation nights per SitePlotYear
# excluded_levels <- c('FF03-OB-2021', 'FF03-OB-2022', 'FF05-OB-2022', 'FF06-OB-2022', 'FF08-OB-2022', 'FF11-OB-2021')
myot <- subset(mydata, manual.id == "MYOT" & behavior %in% c("Feeding", "Commuting")) 
myots <- myot %>% dplyr::filter(!SitePlotYear %in% c('FF03-OB-2021', 'FF03-OB-2022', 'FF05-OB-2022', 'FF06-OB-2022', 'FF08-OB-2022', 'FF11-OB-2021')) %>% droplevels()
myots$II <- myots$InsectIndex
myots$II[myots$II > 2] <- 2 
# from 803 obs to 728

ggplot(myots, aes(x = CanOpen, y = II)) + 
  geom_count(color = "#F57969", size = 3, alpha = 0.7) + 
  stat_poly_line(color = "black") +
  stat_poly_eq() +
  theme_classic() + 
  theme(text = element_text(size=20)) + 
  xlab("Canopy openness") + ylab("Insect index")

ve(path = output_today, filename = "InsectIndexvsCO.tiff", width = 12, height = 8, device='tiff', dpi=600) 

# ## Very similar for bats 
# ggplot(dfs, aes(x = CanOpen, y = batpass)) + 
#   geom_count(color = "#F57969", size = 2, alpha = 0.5) + 
#   stat_poly_line(color = "black") +
#   stat_poly_eq() +
#   theme_minimal() + 
#   xlab("Canopy openness") + ylab("bat passes")

```

## Feeding and Commuting together 
```{r}

head(myots)
summary(myots)
names(myots)
myots$behavior <- factor(myots$behavior)

myots.f <- myots %>% filter(behavior == "Feeding") %>% droplevels()
myots.c <- myots %>% filter(behavior == "Commuting") %>% droplevels()

## II is the same as Insect Index but all values over 2 are converted to 2 

#Using the same model as were best for subset Feeding only
#Adding behavior
m1nb <- gam(batpass ~ s(II, by = behavior) + s(II,CanOpen, by = behavior) + behavior + year + s(Site, bs = "re"), metod="REML", family= "nb()",data = myots)

m2nb <- gam(batpass ~ s(II, CanOpen, by = behavior) + behavior + year + s(Site, bs = "re"), metod="REML", family= "nb()",data = myots)

AIC(m1nb,m2nb)
#        df      AIC
#m1nb 45.04046 3403.364
#m2nb 44.29870 3401.880

summary(m1nb)
summary(m2nb)

par(mfrow = c(2, 2))
gam.check(m1nb) #not horrible, but k values a bit low

par(mfrow = c(2, 2))
gam.check(m2nb) 
 

#######################################################################################
######### Use a 3D plot for the paper #################################################
#######################################################################################

#Predictions
new_data <- expand.grid(
  II = seq(min(myots$II), max(myots$II), length.out = 30),
  CanOpen = unique(myots$CanOpen),
  year = unique(myots$year),
  behavior = unique(myots$behavior),
  Site = unique(myots$Site))

# Make predictions
predictions <- predict(m2nb, new_data, type = "response", se.fit = TRUE)

# Extract predicted values and standard errors
pred_values <- predictions$fit
se <- predictions$se.fit

# Combine predictions with grid data
prediction_data <- cbind(new_data, pred_values, se)

head(prediction_data)
tail(prediction_data)

#I export the predicted data to Excel
# write.table(prediction_data, file = 'predictiondata.csv', col.names = TRUE,
#             row.names = FALSE, sep = ",")

#And import them into R again
# pred <-read.csv("predictiondata.csv",sep=",", dec=".", header=TRUE) #----LOAD THE DATA

pred <- prediction_data

head(pred)
tail(pred)
pred.f <- subset(pred, behavior  == "Feeding")
pred.c <- subset(pred, behavior  == "Commuting")

dim(pred)
dim(pred.f )
dim(pred.c)

range.pred.f <- range(pred.f$pred_values) #[1]  0.005557207 47.581870157
range.pred.c <- range(pred.c$pred_values) #[1]   0.03091761 206.79674714

#Prediction plot for Commuting
# Create a 3D surface plot with rgl
with(pred.c, {
  plot3d(CanOpen, II, matrix(pred_values, ncol = length(unique(pred.c$II))),
         col = terrain.colors(100), type = "h", size = .5, 
         xlab = "Canopy openness", ylab = "Insect index", zlab = "Commuting passes per night",
         main = "",
         cex = 3,
         cex.main = 3, 
         cex.lab = 3) 
  rgl.postscript("3d_plot_commuting.eps", fmt = "eps")
}) 

#Prediction plot for Feeding
# Create a 3D surface plot with rgl
InsectIndex = seq(min(pred.f$II), max(pred.f$II), length.out = 15) 
CanOpen = unique(pred.f$CanOpen)

with(pred.f, {
  plot3d(CanOpen, II, matrix(pred_values, ncol = length(unique(pred.f$II))),
         col = terrain.colors(100), type = "h", size = .5, 
         xlab = "Canopy openness", ylab = "Insect index", zlab = "Feeding passes per night",
         main = "",
         cex = 3,
         cex.main = 3, 
         cex.lab = 3) 
  rgl.postscript("3d_plot_feeding.eps", fmt = "eps")
}) 



### Tally - you can also make this into points by changing to type = "p"

### Now with plot_ly 


### Feeding activity alone 
#########################################################
#z <- matrix(predict(m3nb, newdata = new_data), 374, 50)
InsectIndex = seq(min(pred.f$II), max(pred.f$II), length.out = 15) 
CanOpen = unique(pred.f$CanOpen)


summary(myots$batpass)
summary(pred.f$pred_values) # max = 47
myots.f$batpass1 <- myots.f$batpass
myots.f$batpass1[myots.f$batpass1 > 47] <- 47

myots$batpass1 <- myots$batpass
myots$batpass1[myots$batpass1 > 47] <- 47
# Makes it possible to plot the raw data in the same range as the predictions. 

z <- matrix(pred.f$pred_values, ncol = 5)
plot_ly(x = ~CanOpen, y = ~InsectIndex, z = z, type = "surface") %>%
  layout(
    scene = list(
      xaxis = list(title = "Canopy openness"),
      yaxis = list(title = "Insect index"),
      zaxis = list(title = "Feeding passes per night"))) %>%  
  #option to plot with raw(ish) data
  add_markers(x = ~myots.f$CanOpen, y= ~myots.f$II, z=myots.f$batpass1) 

# ggsave(path = output_today, filename = "FeedingGAM_Results_Pred.tiff", width = 12, height = 8, device='tiff', dpi=600) 


### Commuting activity alone 
#########################################################
#z <- matrix(predict(m3nb, newdata = new_data), 374, 50)
InsectIndex = seq(min(pred.c$II), max(pred.c$II), length.out = 15) 
CanOpen = unique(pred.c$CanOpen)


summary(myots$batpass)
summary(pred.c$pred_values) # max = 47
myots.c$batpass1 <- myots.c$batpass
myots.c$batpass1[myots.c$batpass1 > 200] <- 200
# Makes it possible to plot the raw data in the same range as the predictions. 
11220/30

z <- matrix(pred.c$pred_values, ncol = 20)
plot_ly(x = ~CanOpen, y = ~InsectIndex, z = z, type = "surface") %>%
  layout(
    scene = list(
      xaxis = list(title = "Canopy openness"),
      yaxis = list(title = "Insect index"),
      zaxis = list(title = "Feeding passes per night"))) %>%  
  #option to plot with raw(ish) data
  add_markers(x = ~myots.c$CanOpen, y= ~myots.c$II, z=myots.c$batpass1) 

# ggsave(path = output_today, filename = "FeedingGAM_Results_Pred.tiff", width = 12, height = 8, device='tiff', dpi=600) 


```


## Tally 

The predictions I am plotting with plot_ly do not quite match up with the raw data or the model predictions made using the rgl package. I am pretty sure it has to do with how I define the predicted values in plot_ly (the "z" value) as a matrix but not sure if there are other settings in the plot that I should be adjusting. Would be very curious to hear your thoughts on this. 
